---
title: "sitemap_scraper"
author: "Zorbey Özcan"
date: "2025-05-24"
output: html_document
---

# Overview of the Sitemap Scraper Workflow

This R Markdown document implements a structured, multi-stage scraping pipeline designed to identify, extract, and validate sitemap URLs from a predefined set of German-language news media domains. The primary objective is to support reproducible research in the social sciences by enabling scalable and systematic collection of article-level metadata via publicly accessible sitemap structures.

The workflow is organized into a sequence of clearly defined steps, beginning with domain collection, followed by the retrieval of `robots.txt` files, extraction and validation of sitemap URLs, and culminating in a rigorous filtering and export process. Each code chunk performs a specific role in this pipeline and is annotated with precise comments to facilitate replication.

The pipeline employs a combination of HTTP requests, regular expressions, content parsing, and logical filtering operations. Intermediate results are stored and debugged where necessary, and the environment is cleaned at the end to ensure transparency and memory efficiency. The final outputs are exported as structured `.csv` files that distinguish between successfully retrieved sitemaps and those excluded due to irrelevance or error.

```{r Preparation}
# knitting Options 
knitr::opts_chunk$set(
  echo    = TRUE,       
  results = 'hide',  
  message = FALSE,  
  warning = FALSE    
)
library(httr)
library(dplyr)
library(tidyr)
library(rmarkdown)
library(rvest)
```

## Code Chunk: Retrieving Input Data from GitHub Repository

### Summary:
This code chunk initializes the scraping workflow by retrieving a structured list of domains from a publicly available GitHub repository. The HTML content of the specified GitHub page is parsed to extract embedded tables, from which a subset of German-language media domains is selected. This serves as the input foundation for all subsequent steps in the pipeline.

**Inputs:**  
- HTML content from the GitHub page at `https://github.com/JBGruber/paperboy`, specifically the sixth `<table>` element.

**Outputs:**  
- A cleaned data frame `global_input_all_domains`, which contains a single column `domain_url` listing filtered German news domains.  
- A minor data correction is applied to handle a duplicated `.de` domain artifact.

```{r Retrieving input data }
# Define the GitHub URL
step_0_url <- "https://github.com/JBGruber/paperboy"

# Read the HTML content of the page
step_0_page <- read_html(step_0_url)

# Extract all tables from the HTML
step_0_tables_list <- step_0_page %>% html_elements("table")

# Convert the sixth table to a data frame
global_input_all_domains <- step_0_tables_list[[6]] %>% html_table()

# Filter rows where the domain column contains ".de", "postillion", or "finanzen" for all german newsmedia
global_input_all_domains <- global_input_all_domains %>%
  filter(grepl("\\.de|postillion|finanzen|faz", domain, ignore.case = TRUE)) %>%
  select(domain_url = domain)

# Correct the domain entry with a duplicated ".de"
global_input_all_domains <- global_input_all_domains %>%
  mutate(domain_url = ifelse(domain_url == "abendzeitung-muenchen.de.de", 
                             "abendzeitung-muenchen.de", 
                             domain_url))

```

## Code Chunk: Step 1 – Retrieval of robots.txt URLs from Input Domains

### Summary:
This code chunk attempts to locate a valid `robots.txt` file for each input domain using various protocol permutations (HTTP, HTTPS, and HTTPS with `www`). It aims to construct and validate accessible URLs for each domain’s `robots.txt` file. Domains for which no valid `robots.txt` is found are flagged for debugging.

**Inputs:**  
- The data frame `global_input_all_domains`, containing a list of domain names to be tested.

**Outputs:**  
- `step_1_domain_urls_robotsUrls_df`: A data frame mapping each domain to a discovered (or missing) `robots.txt` URL.  
- `step_1_1_debug_unsuccsesful_fetches_df`: A debug table listing domains for which no valid `robots.txt` could be retrieved.  
- Summary metrics on the success rate of URL discovery are printed to the console.

#### Function: `step_1_robots_url_func`
This function receives a domain name and returns the first accessible URL that hosts a valid `robots.txt` file. It constructs three potential URLs for each domain using:
1. `http://domain/robots.txt`
2. `https://domain/robots.txt`
3. `https://www.domain/robots.txt`

Each URL is checked using an HTTP `HEAD` request. If the response status code is `200`, the URL is considered valid and returned. If none of the three URLs return a valid response, the function returns `NA`. The function uses `tryCatch()` to handle request errors gracefully and ensures robustness across domains with different protocol configurations.

#### Function: `step_1_get_robots_url_func`
This is a vectorized wrapper around `step_1_robots_url_func`, allowing the function to be applied to multiple domain names simultaneously. It enables efficient processing of the full domain list while preserving the individual logic of the core retrieval function.

```{r Step 1 }
# Function to retrieve robots.txt URL from a domain using different protocols
step_1_robots_url_func <- function(step_1_domain_url) {
  # Construct possible robots.txt URLs for HTTP, HTTPS, and HTTPS with www
  step_1_robots_http_url <- paste0("http://", step_1_domain_url, "/robots.txt")
  step_1_robots_https_url <- paste0("https://", step_1_domain_url, "/robots.txt")
  step_1_robots_www_https_url <- paste0("https://www.", step_1_domain_url, "/robots.txt")

  # Initialize variables to store responses
  step_1_response_http <- NULL
  step_1_response_https <- NULL
  step_1_response_www_https <- NULL

  # Attempt to fetch the robots.txt file using HTTP
  step_1_response_http <- tryCatch(
    {
      httr::HEAD(step_1_robots_http_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Attempt to fetch the robots.txt file using HTTPS
  step_1_response_https <- tryCatch(
    {
      httr::HEAD(step_1_robots_https_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Attempt to fetch the robots.txt file using HTTPS with www
  step_1_response_www_https <- tryCatch(
    {
      httr::HEAD(step_1_robots_www_https_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Check and return the first valid robots.txt URL found
  if (!is.null(step_1_response_http) && step_1_response_http$status_code == 200) {
    print(paste("Returning HTTP robots.txt URL:", step_1_robots_http_url))
    return(step_1_robots_http_url)
  } else if (!is.null(step_1_response_https) && step_1_response_https$status_code == 200) {
    print(paste("Returning HTTPS robots.txt URL:", step_1_robots_https_url))
    return(step_1_robots_https_url)
  } else if (!is.null(step_1_response_www_https) && step_1_response_www_https$status_code == 200) {
    print(paste("Returning HTTPS www robots.txt URL:", step_1_robots_www_https_url))
    return(step_1_robots_www_https_url)
  } else {
    print("No valid robots.txt URL found. Returning NA.")
    return(NA)
  }
}

# Vectorize the function for processing multiple domains
step_1_get_robots_url_func <- Vectorize(step_1_robots_url_func)

# Create a new DataFrame for storing robots.txt URLs
step_1_domain_urls_robotsUrls_df <- global_input_all_domains

# Add a new column with robots.txt URLs using the vectorized function
step_1_domain_urls_robotsUrls_df$robots_txt <- step_1_get_robots_url_func(step_1_domain_urls_robotsUrls_df$domain_url)

# Count the total number of domains and valid robots.txt URLs
step_1_total_domains_check <- nrow(step_1_domain_urls_robotsUrls_df)
step_1_valid_robots_check <- sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt))

# Print the summary of the robots.txt retrieval
if (step_1_valid_robots_check == step_1_total_domains_check) {
  print(paste(step_1_valid_robots_check, "of", step_1_total_domains_check, "robots.txt URLs found"))
} else {
  print(paste(step_1_valid_robots_check, "of", step_1_total_domains_check, "robots.txt URLs found. Some are missing."))
}

# Debug function to create a DataFrame for unsuccessful robots.txt fetches
if (step_1_valid_robots_check != step_1_total_domains_check) {
  # Create a debug DataFrame with domains where robots.txt was not found
  step_1_1_debug_unsuccsesful_fetches_df <- step_1_domain_urls_robotsUrls_df %>%
    filter(is.na(robots_txt)) %>%  # Filter rows where robots.txt is NA
    select(domain_url, robots_txt)  # Include relevant columns for debugging

  # Add a column to indicate that no robots.txt was found
  step_1_1_debug_unsuccsesful_fetches_df <- step_1_1_debug_unsuccsesful_fetches_df %>%
    mutate(
      issue = "No valid robots.txt URL found"
    )

  # Print confirmation
  print(paste("Created step_1_1_debug_unsuccsesful_fetches_df with", nrow(step_1_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}


```

## Code Chunk: Step 2 – Retrieval of robots.txt File Contents

### Summary:
This code chunk proceeds to download the actual contents of the `robots.txt` files for each domain whose URL was successfully identified in Step 1. For each valid URL, the content is requested via an HTTP `GET` call and stored as a plain text string. If the file is inaccessible or an error occurs, a missing value (`NA`) is recorded. Unsuccessful retrievals are systematically logged for debugging.

**Inputs:**  
- The `robots_txt` column from `step_1_domain_urls_robotsUrls_df`, containing discovered `robots.txt` URLs.

**Outputs:**  
- `step_2_domain_Urls_robotsUrls_robotsContents_df`: A new data frame that includes the `robots_txt_content` column with raw text contents.  
- `step_2_1_debug_unsuccsesful_fetches_df`: A diagnostic data frame listing all failed attempts, including HTTP status codes and error metadata.

#### Function: `step_2_robots_txt_content_func`
This function attempts to download and return the textual content of a specified `robots.txt` URL. First, it checks the URL’s availability via a `HEAD` request and prints its HTTP status code for transparency. If accessible (status code 200), the full file is fetched using a `GET` request with UTF-8 encoding. If any error occurs during connection or content retrieval, `NA` is returned. The function is wrapped in `tryCatch()` to handle network or timeout exceptions robustly, ensuring the scraping workflow remains uninterrupted.

```{r Step 2 }
# Function to retrieve the content of a robots.txt file given its URL
step_2_robots_txt_content_func <- function(step_2_url) {
  # Check the HTTP status of the URL
  step_2_response <- tryCatch(
    {
      httr::HEAD(step_2_url, timeout(5))  # Check the HEAD response for the URL
    },
    error = function(e) NULL
  )

  # Debugging: Print the HTTP status or connection error
  if (!is.null(step_2_response)) {
    print(paste("HTTP status for", step_2_url, ":", step_2_response$status_code))
    if (step_2_response$status_code == 200) {
      print(paste("robots.txt successfully found for:", step_2_url))
    }
  } else {
    print(paste("Error: Unable to connect to", step_2_url))
  }

  # Fetch and return the content of the robots.txt file if accessible
  tryCatch(
    {
      httr::GET(step_2_url) %>% content("text", encoding = "UTF-8")  # Get the full content
    },
    error = function(e) NA  # Return NA if any error occurs
  )
}

# Apply the function to each URL and store the results in a new DataFrame
step_2_domain_Urls_robotsUrls_robotsContents_df <- step_1_domain_urls_robotsUrls_df %>%
  mutate(
    robots_txt_content = sapply(robots_txt, step_2_robots_txt_content_func)
  )

# Calculate the total number of domains and valid robots.txt content entries
step_2_total_domains_check <- nrow(step_1_domain_urls_robotsUrls_df)
step_2_valid_contents_check <- sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content))

# Print the summary of the robots.txt content retrieval
if (step_2_valid_contents_check == step_2_total_domains_check) {
  print(paste(step_2_valid_contents_check, "of", step_2_total_domains_check, "robots.txt contents successfully fetched"))
} else {
  print(paste(step_2_valid_contents_check, "of", step_2_total_domains_check, "robots.txt contents fetched. Some are missing."))
}

# Debug function to create a DataFrame for unsuccessful robots.txt content fetches
if (step_2_valid_contents_check != step_2_total_domains_check) {
  # Create a debug DataFrame with domains where robots.txt content was not successfully fetched
  step_2_1_debug_unsuccsesful_fetches_df <- step_2_domain_Urls_robotsUrls_robotsContents_df %>%
    filter(is.na(robots_txt_content)) %>%  # Filter rows where robots.txt content is NA
    mutate(
      http_status = sapply(robots_txt, function(url) {
        response <- tryCatch(
          {
            httr::HEAD(url, timeout(5))
          },
          error = function(e) NULL
        )
        if (!is.null(response)) {
          return(response$status_code)  # Return the HTTP status code if available
        } else {
          return("Error")  # Indicate an error if no response
        }
      }),
      issue = "robots.txt content not fetched"  # Indicate the issue
    ) %>%
    select(domain_url, robots_txt, http_status, issue)  # Include relevant columns for debugging

  # Print confirmation
  print(paste("Created step_2_1_debug_unsuccsesful_fetches_df with", nrow(step_2_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}

```

## Code Chunk: Step 3 – Extraction of Sitemap URLs from robots.txt Files

### Summary:
This code chunk extracts sitemap URLs directly from the textual content of each domain's `robots.txt` file. It applies a regular expression to identify and isolate any declared sitemap locations. The results are appended to the main data frame and classified based on the number of sitemaps discovered. This provides the first structured insight into the domains' indexing architectures.

**Inputs:**  
- The column `robots_txt_content` from the data frame `step_2_domain_Urls_robotsUrls_robotsContents_df`.

**Outputs:**  
- `step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df`: A data frame extended with one row per extracted sitemap URL and a `sitemap_check` classification label.  
- Console summary of domains with and without declared sitemap URLs.

#### Function: `step_3_extract_sitemap_urls_func`
This function extracts one or more sitemap URLs from a `robots.txt` content string. The content is first sanitized by collapsing line breaks into spaces to ensure pattern matching continuity. A case-insensitive regular expression is applied to identify all instances of the `Sitemap:` directive followed by an HTTP/HTTPS URL. The prefix is removed, and only unique sitemap links are returned. If no match is found, the function returns `NA`. The function operates independently of line structure, making it robust against inconsistent formatting.

```{r Step 3 }
# Function to extract sitemap URLs from robots.txt content
step_3_extract_sitemap_urls_func <- function(step_3_content) {
  # Remove line breaks and replace with spaces
  step_3_clean_content <- gsub("[\r\n]+", " ", step_3_content)

  # Regular expression to identify sitemap URLs, case-insensitive
  step_3_sitemap_pattern <- "(?i)sitemap:\\s*(https?://[\\w./~:-]+)"

  # Extract all matching URLs
  step_3_sitemaps <- regmatches(step_3_clean_content, gregexpr(step_3_sitemap_pattern, step_3_clean_content, perl = TRUE))[[1]]

  # Remove the "sitemap:" prefix from results
  step_3_sitemaps <- gsub("(?i)sitemap[:\\s]+", "", step_3_sitemaps, perl = TRUE)

  # Return unique URLs or NA if none found
  if (length(step_3_sitemaps) == 0) {
    return(NA)
  } else {
    return(unique(step_3_sitemaps))
  }
}

# Expand the DataFrame by adding sitemap URLs and related information
step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df <- step_2_domain_Urls_robotsUrls_robotsContents_df %>%
  mutate(
    sitemap_URLs = lapply(robots_txt_content, function(step_3_content) {
      if (is.na(step_3_content)) {
        return(NA)  # Return NA if no robots.txt content is available
      } else {
        return(step_3_extract_sitemap_urls_func(step_3_content))  # Extract sitemap URLs
      }
    }),
    sitemap_check = case_when(
      is.na(sitemap_URLs) ~ "no sitemap",                          # No sitemaps found
      lengths(sitemap_URLs) == 1 ~ "one sitemap",                  # One sitemap found
      lengths(sitemap_URLs) > 1 ~ "multiple sitemaps"              # Multiple sitemaps found
    )
  ) %>%
  tidyr::unnest(sitemap_URLs, keep_empty = TRUE) %>%  # Flatten lists and keep empty entries
  rename(sitemap_URL = sitemap_URLs)  # Rename the column for clarity

# Calculate the total number of sitemap URLs and domains with/without sitemaps
step_3_total_sitemaps_check <- sum(!is.na(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_URL))
step_3_domains_with_sitemaps_check <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check != "no sitemap") %>%
  distinct(domain_url) %>%
  nrow()
step_3_domains_without_sitemaps_check <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check == "no sitemap") %>%
  distinct(domain_url) %>%
  nrow()

# Print the summary of sitemap extraction
print(paste("Total sitemap URLs found:", step_3_total_sitemaps_check))
print(paste("Unique domains with sitemap URLs:", step_3_domains_with_sitemaps_check))
print(paste("Unique domains without sitemap URLs:", step_3_domains_without_sitemaps_check))

```

## Code Chunk: Step 4 – Heuristic Discovery of Typical Sitemap URLs

### Summary:
This step addresses cases where no sitemap URLs were explicitly declared in the `robots.txt` files. It implements a heuristic strategy by testing a predefined list of commonly used sitemap URL paths against each domain. Valid responses (HTTP status 200) are collected and integrated into the main dataset, thereby extending coverage to domains with implicit or undeclared sitemap structures.

**Inputs:**  
- The data frame `step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df`, filtered for domains lacking sitemap declarations (`sitemap_check == "no sitemap"`).  
- A predefined vector `step_4_typical_sitemap_paths_vec` containing commonly observed sitemap path suffixes.

**Outputs:**  
- `step_4_1_missing_sitemaps_df`: A table of newly discovered sitemap URLs for domains that originally had none.  
- `step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df`: The consolidated dataset, updated with both explicitly and heuristically found sitemap URLs.  
- Console diagnostics reporting total, new, and unresolved sitemap discoveries.

#### Function: `step_4_find_typical_sitemaps_func`
This function attempts to discover valid sitemap URLs by appending a series of typical path suffixes to a given domain. For each constructed URL (e.g., `https://domain.com/sitemap.xml`), the function sends an HTTP `HEAD` request and evaluates the response. If the status code is 200, the URL is considered valid and appended to the result. The function is robust against network errors via `tryCatch()` and can return multiple sitemap links per domain. It supports exhaustive scanning for standardized but undeclared sitemap locations across diverse site structures.

```{r Step 4 }
# Define typical sitemap paths
step_4_typical_sitemap_paths_vec <- c(
  "/sitemap.xml", "/sitemap_index.xml", "/sitemap-index.xml", "/sitemaps/sitemap.xml",
  "/sitemaps/sitemap_index.xml", "/sitemap-posts.xml", "/sitemap-pages.xml",
  "/sitemap-products.xml", "/sitemap-2025-01.xml", "/sitemap-2024.xml",
  "/sitemap-images.xml", "/sitemap-videos.xml", "/sitemap-en.xml",
  "/sitemap-de.xml", "/sitemap.php", "/sitemap.txt", "/sitemap.xml.gz",
  "/sitemap/", "/sitemapindex.xml", "/sitemap/index.xml", "/sitemap1.xml",
  "/~/sitemap.xml", "/~/sitemap_index.xml", "/~/sitemap-index.xml",
  "/~/sitemaps/sitemap.xml", "/~/sitemaps/sitemap_index.xml", "/~/sitemap-posts.xml",
  "/~/sitemap-pages.xml", "/~/sitemap-products.xml", "/~/sitemap-2025-01.xml",
  "/~/sitemap-2024.xml", "/~/sitemap-images.xml", "/~/sitemap-videos.xml",
  "/~/sitemap-en.xml", "/~/sitemap-de.xml", "/~/sitemap.php", "/~/sitemap.txt",
  "/~/sitemap.xml.gz", "/~/sitemap/", "/~/sitemapindex.xml", "/~/sitemap/index.xml",
  "/~/sitemap1.xml"
)

# Function to check typical sitemap URLs for a given domain
step_4_find_typical_sitemaps_func <- function(step_4_domain) {
  step_4_valid_sitemaps <- c()  # List to store found sitemaps

  for (step_4_path in step_4_typical_sitemap_paths_vec) {
    step_4_url <- paste0("https://", step_4_domain, step_4_path)  # Construct full URL
    step_4_response <- tryCatch(
      {
        httr::HEAD(step_4_url, timeout(5))  # HTTP HEAD request
      },
      error = function(e) NULL
    )

    if (!is.null(step_4_response)) {
      # Print HTTP status for debugging
      print(paste("HTTP status for", step_4_url, ":", step_4_response$status_code))

      # Check if the sitemap is valid (status code 200)
      if (step_4_response$status_code == 200) {
        print(paste("Valid sitemap found for domain", step_4_domain, ":", step_4_url))
        step_4_valid_sitemaps <- c(step_4_valid_sitemaps, step_4_url)
      }
    } else {
      print(paste("Error: Unable to connect to", step_4_url))
    }
  }

  return(step_4_valid_sitemaps)  # Return all found sitemaps
}

# Create a new DataFrame for domains with no sitemaps
step_4_1_missing_sitemaps_df <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check == "no sitemap") %>%
  distinct(domain_url) %>%
  mutate(
    sitemap_URL = NA,            # Add column for found sitemaps
    sitemap_check = "no sitemap" # Initial status
  )

# Search for typical sitemaps and update the DataFrame
step_4_1_missing_sitemaps_df <- step_4_1_missing_sitemaps_df %>%
  rowwise() %>%
  mutate(
    found_sitemaps = list(step_4_find_typical_sitemaps_func(domain_url))  # Find typical sitemaps
  ) %>%
  tidyr::unnest(found_sitemaps, keep_empty = TRUE) %>%
  mutate(
    sitemap_URL = ifelse(is.na(found_sitemaps), NA, found_sitemaps),  # Add found sitemaps
    sitemap_check = ifelse(is.na(found_sitemaps), "no sitemap", "found typical sitemap")
  ) %>%
  select(domain_url, sitemap_URL, sitemap_check)  # Keep relevant columns

# Merge original and new results into the final DataFrame
step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  left_join(
    step_4_1_missing_sitemaps_df %>%
      filter(!is.na(sitemap_URL)),  # Only include new sitemaps
    by = "domain_url",
    suffix = c("", "_new")
  ) %>%
  mutate(
    sitemap_URL = coalesce(sitemap_URL_new, sitemap_URL),          # Merge URLs
    sitemap_check = coalesce(sitemap_check_new, sitemap_check)    # Merge status
  ) %>%
  select(-ends_with("_new"))  # Remove helper columns

# Check: Print results for validation
step_4_total_domains_check <- nrow(step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df)
step_4_total_sitemaps_check <- sum(!is.na(step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df$sitemap_URL))
step_4_domains_with_sitemaps_check <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  filter(!is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()
step_4_domains_without_sitemaps_check <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  filter(is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()
step_4_new_sitemaps_added_check <- step_4_1_missing_sitemaps_df %>%
  filter(!is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()

print(paste("Total sitemap URLs found:", step_4_total_sitemaps_check))
print(paste("Unique domains with sitemap URLs:", step_4_domains_with_sitemaps_check))
print(paste("Unique domains without sitemap URLs:", step_4_domains_without_sitemaps_check))
print(paste("This step added", step_4_new_sitemaps_added_check, "sitemap URLs"))

```

## Code Chunk: Step 5 – Retrieval of Sitemap File Contents

### Summary:
This step downloads the full content of each discovered sitemap URL. Using HTTP `GET` requests, it attempts to retrieve both regular XML files and compressed `.gz` variants. For each sitemap, the raw content and associated HTTP status code are extracted. If content retrieval fails, detailed metadata are logged for diagnostic purposes, allowing identification of inaccessible or corrupted sitemap files.

**Inputs:**  
- The column `sitemap_URL` from the merged data frame `step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df`, which includes both explicitly declared and heuristically discovered sitemap links.

**Outputs:**  
- `step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents`: A data frame including raw `sitemap_content` and `http_status` metadata for each sitemap URL.  
- `step_5_1_debug_unsuccsesful_fetches_df`: A debug file capturing all failed retrievals with indicators of whether the failed URL was the only sitemap associated with a given domain.

#### Function: `step_5_get_sitemap_content_func`
This function downloads and processes the content of a given sitemap URL. If the input URL is `NA`, it returns a placeholder result. For valid URLs, the function executes an HTTP `GET` request with a 120-second timeout. If the sitemap is a `.gz`-compressed file, the binary content is decompressed using `gzcon()` and then read as plain text. Non-compressed sitemaps are handled via direct UTF-8 decoding. The function returns a named list containing both the `content` (text) and `status` (HTTP status code or error message). All errors are managed via `tryCatch()` to ensure resilience against network issues, malformed files, and unsupported content types.

```{r Step 5 }
# Function to fetch the content of a sitemap URL and capture the HTTP status or errors
step_5_get_sitemap_content_func <- function(step_5_url) {
  if (is.na(step_5_url)) {
    print("Sitemap URL is NA, skipping...")
    return(list(content = NA, status = "NA"))  # Return NA for content and status
  }

  step_5_result <- tryCatch(
    {
      step_5_response <- httr::GET(step_5_url, timeout(120))  # HTTP GET request with timeout
      print(paste("Fetching sitemap for URL:", step_5_url, "Status code:", step_5_response$status_code))
      
      if (step_5_response$status_code == 200) {
        # Check if the URL points to a .gz file
        if (grepl("\\.gz$", step_5_url, ignore.case = TRUE)) {
          print("Detected .gz sitemap, attempting to decompress...")

          # Retrieve raw binary content
          raw_content <- httr::content(step_5_response, as = "raw")  
          
          # Decompress the .gz content using gzcon()
          con <- gzcon(rawConnection(raw_content))
          xml_text <- readLines(con, warn = FALSE)
          close(con)
          
          # Return the extracted XML content
          list(content = paste(xml_text, collapse = "\n"), status = step_5_response$status_code)
          
        } else {
          # Standard handling for non-gzipped sitemaps
          list(content = httr::content(step_5_response, "text", encoding = "UTF-8"), status = step_5_response$status_code)
        }
        
      } else {
        print(paste("Failed to fetch sitemap for URL:", step_5_url, "Status code:", step_5_response$status_code))
        list(content = NA, status = step_5_response$status_code)
      }
    },
    error = function(e) {
      print(paste("Error fetching sitemap for URL:", step_5_url))
      list(content = NA, status = "Error")  # Capture error as status
    }
  )

  return(step_5_result)
}

# Copy the DataFrame and add columns for sitemap content and status
step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  mutate(
    result = lapply(sitemap_URL, step_5_get_sitemap_content_func),  # Fetch the content and status
    sitemap_content = sapply(result, function(x) x$content),        # Extract content
    http_status = sapply(result, function(x) x$status)             # Extract HTTP status or error
  ) %>%
  select(-result)  # Remove the intermediate result column

# Check: Only consider rows with a valid sitemap_URL
step_5_valid_sitemaps_check <- step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents %>%
  filter(!is.na(sitemap_URL))

step_5_total_valid_sitemaps_check <- nrow(step_5_valid_sitemaps_check)
step_5_loaded_valid_sitemaps_check <- sum(!is.na(step_5_valid_sitemaps_check$sitemap_content))

print(paste("Total sitemap URLs with valid links:", step_5_total_valid_sitemaps_check))
print(paste(step_5_loaded_valid_sitemaps_check, "of", step_5_total_valid_sitemaps_check, "sitemaps were loaded successfully"))

# If not all valid sitemaps were fetched successfully, create a debug DataFrame
if (step_5_loaded_valid_sitemaps_check != step_5_total_valid_sitemaps_check) {
  # Identify domains with at least one successfully fetched sitemap
  domains_with_successful_sitemaps <- step_5_valid_sitemaps_check %>%
    filter(!is.na(sitemap_content)) %>%
    pull(domain_url)
  
  # Create the debug DataFrame
  step_5_1_debug_unsuccsesful_fetches_df <- step_5_valid_sitemaps_check %>%
    filter(is.na(sitemap_content)) %>%
    mutate(
      is_only_sitemap = !domain_url %in% domains_with_successful_sitemaps  # Check if this is the only sitemap for the domain
    ) %>%
    select(domain_url, sitemap_URL, http_status, is_only_sitemap)  # Include status and exclusivity in debug

  print(paste("Created step_5_1_debug_unsuccsesful_fetches_df with", nrow(step_5_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}

```

## Code Chunk: Step 6 – Cleaning, Filtering, and Exporting the Final Sitemap Dataset

### Summary:
This step performs a comprehensive filtering process to remove sitemap URLs that are either irrelevant, erroneous, or unsuitable for further analysis. Multiple exclusion criteria are applied, including the presence of multimedia-only content, HTML instead of XML format, dynamic domains without proper sitemap structures, and manually identified non-article sources. The remaining valid entries are assigned unique IDs and exported as structured CSV files for further processing or replication.

**Inputs:**  
- The data frame `step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents`, which contains raw sitemap contents and associated metadata.

**Outputs:**  
- `step_6_cleaned_df`: The cleaned and filtered dataset of valid sitemaps.  
- `p1_all_sitemaps.csv`: Export of both valid and excluded entries.  
- `sitemap_scraper_clean_sitemaps.csv`: The main cleaned output containing only valid, article-relevant sitemaps.  
- `p1_excluded_sitemaps.csv`: A summary of all excluded entries, categorized by reason.

### Filter Logic:
1. **Media-Only Sitemaps:** Removed if the URL suggests image, video, podcast, or audio content (`filtered_media_sitemaps_df`).
2. **Irrelevant Structures:** Excluded based on patterns such as author listings, sports pages, shops, or admin pages (`filtered_irrelevant_sitemaps_df`).
3. **HTML Content:** Removed if sitemap content includes HTML declarations instead of XML (`filtered_html_sitemaps_df`).
4. **Dynamic/Non-Static Domains:** Manually excluded domains identified as JavaScript-driven or broadcast-only platforms (`filtered_dynamic_sitemaps_df`).
5. **Manually Verified Global Exclusions:** Explicit URLs known to contain non-article resources like tags, finance tickers, or advertisement indexes (`filtered_global_step_6_excluded_sitemaps_df`).
6. **Missing Data:** Entries with missing sitemap URLs or contents are also excluded and logged (`missing_sitemap_url`, `missing_sitemap_content`).

All filtered entries are consolidated into `export_broken_sitemaps`, and a final filtered dataset is assigned per-domain unique IDs and exported in multiple forms. Summary statistics are printed for transparency and traceability.

```{r Step 6 }
# Step 6: Clean and export final sitemap dataset
step_6_cleaned_df <- step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents

# Assign a unique domainID to each unique domain
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(domainID = as.numeric(factor(domain_url)))  # Each unique domain gets a unique ID

# Step 6.1 - Filter Media Sitemaps - These contain links to pictures, videos and podcasts exclusively
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl(paste(c("image","bilder", "picture", "fotografie", "photo", "foto", "imagegallery", "gallery", "video", "media", "audio", "podcasts", "podcast" ), collapse = "|"), sitemap_URL, ignore.case = TRUE), "media_sitemaps", NA))

filtered_media_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_media_sitemaps_df), "entries had media-related sitemaps and have been filtered"))

# Step 6.2 - Filter other unrelevant sitemaps 
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl(paste(c( "themen.*-az", # these contain topics and not articles
                                                  "author",      # these contain author pages and not articles
                                                  "sport",       # these contain sports and live broacasts and not articles
                                                  "shop",        # these contain shop elements and not articles
                                                  "security"),   # these contain administrative sitemaps and not articles
                                                  collapse = "|"), sitemap_URL, ignore.case = TRUE),
                                                  "irrelevant_sitemaps", NA))

filtered_irrelevant_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_irrelevant_sitemaps_df), "entries had other non related sitemaps and have been filtered"))


# Step 6.3 - Filter HTML Contents
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl("<!DOCTYPE html", sitemap_content, ignore.case = TRUE), "html contents", NA))

filtered_html_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_html_sitemaps_df), "entries had HTML contents in sitemap and have been filtered"))

# Step 6.4 - Filter Dynamic Websites which do not rely on sitemaps 
# (I verified those as dynamic websites manually by disabeling java script in my browser and using the free browser plug in "Wappalyzer")
# (Other domains are TV or radio channels, which carry TV Shows and podcasts, but not articles) 
blocked_domains <- c(
  "dnn.de", "express.de", "focus.de", "haz.de", "ksta.de", "lvz.de",
  "maz-online.de", "ostsee-zeitung.de", "rbb24.de", "rnd.de",
  "ruhrnachrichten.de", "saechsische.de", 
  # tv channels and radio:
  "deutschlandfunk.de","deutschlandfunkkultur.de", "kabeleins.de", "prosieben.de", "vox.de"
)

step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(domain_url %in% blocked_domains, "dynamic websites", NA))

filtered_dynamic_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_dynamic_sitemaps_df), "entries were filtered as dynamic websites"))

# Step 6.5 - Filter Global Excluded Sitemaps (manually verified non-article sources)
# These are structurally valid but contain only keywords, finance data, cities or technical indexes.
excluded_sitemaps <- c(
  "https://www.nw.de/_retresco/sitemap/index.xml",                   # this sitemap contains topics and not articles
  "https://www.presseportal.de/sitemap-de-index-keywords.xml",       # this sitemap contains keywords and not articles
  "https://www.presseportal.de/sitemap-de-index-newsrooms.xml",      # this sitemap contains advertisements and not articles
  "https://www.presseportal.de/sitemap-de-index-cities.xml",         # this sitemap contains topics by region and not articles
  "https://www.tag24.de/sitemap_tag24_d.xml",                        # this sitemap contains deleted articles 
  "https://www.finanzen.net/sitemap/sitemap.xml",                    # this sitemap contains financial news tickers and not articles
  "https://www.finanzen.net/xml/google-sitemaps/google_sitemap.xml", # this sitemap contains financial news tickers and not articles
  "https://www.finanzen.net/ratgeber/sitemap_index.xml"              # this sitemap contains financial news tickers and not articles
)

# Filter entries matching the global exclusion list
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(sitemap_URL %in% excluded_sitemaps, "excluded_sitemaps", NA))

# Create filtered DataFrame
filtered_global_step_6_excluded_sitemaps_df <- step_6_cleaned_df %>%
  filter(!is.na(filtered_because))

# Remove excluded entries from the main DataFrame
step_6_cleaned_df <- step_6_cleaned_df %>%
  filter(is.na(filtered_because)) %>%
  select(-filtered_because)

# Output summary
print(paste(nrow(filtered_global_step_6_excluded_sitemaps_df), "entries had other non related content"))

# Remove entries with missing sitemap_URL and create missing_sitemap_url df
missing_sitemap_url <- step_6_cleaned_df %>% filter(is.na(sitemap_URL)) %>% mutate(filtered_because = "missing sitemap URL")
step_6_cleaned_df <- step_6_cleaned_df %>% filter(!is.na(sitemap_URL))
print(paste(nrow(missing_sitemap_url), "entries had missing sitemap_URL and have been removed"))

# Remove entries with missing sitemap_content and create missing_sitemap_content df
missing_sitemap_content <- step_6_cleaned_df %>% filter(is.na(sitemap_content)) %>% mutate(filtered_because = "missing sitemap content")
step_6_cleaned_df <- step_6_cleaned_df %>% filter(!is.na(sitemap_content))
print(paste(nrow(missing_sitemap_content), "entries had missing sitemap_content and have been removed"))

# Combine missing_sitemap_url and missing_sitemap_content into failed_sitemaps
failed_sitemaps <- bind_rows(missing_sitemap_url, missing_sitemap_content)
print(paste(nrow(failed_sitemaps), "entries are in the failed_sitemaps dataset"))

# Combine all filtered datasets into export_broken_sitemaps
export_broken_sitemaps <- bind_rows(
  filtered_media_sitemaps_df, 
  filtered_html_sitemaps_df, 
  filtered_dynamic_sitemaps_df,
  failed_sitemaps
)

# Adjusting sitemap_check
step_6_cleaned_df <- step_6_cleaned_df %>%
  group_by(domain_url) %>%
  mutate(sitemap_check = ifelse(n() == 1, "one sitemap", "multiple sitemaps")) %>%
  ungroup()

### Exporting all data:

# p1 all sitemaps: 
p1_all_sitemaps <- bind_rows(step_6_cleaned_df, export_broken_sitemaps)
write.csv(p1_all_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_all_sitemaps.csv", row.names = FALSE)

# p1 clean sitemaps: 
sitemap_scraper_clean_sitemaps <- step_6_cleaned_df %>%
  transmute(
    domain_id = as.numeric(factor(domain_url)),         
    domain_url = domain_url,
    layer_1_url = sitemap_URL
  ) %>%
  mutate(layer_1_url_id = row_number()) %>%            
  select(domain_id, domain_url, layer_1_url_id, layer_1_url)
write.csv(sitemap_scraper_clean_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/data/sitemap_scraper_clean_sitemaps.csv", row.names = FALSE) 


# p1 excluded sitemaps:
p1_excluded_sitemaps <- bind_rows(
  
  filtered_media_sitemaps_df  %>% mutate(reason = "media sitemap - images, videos, podcasts"),
  filtered_irrelevant_sitemaps_df %>% mutate(reason = "irrelevant sitemap - e.g. authors, shop, sport"),
  filtered_html_sitemaps_df  %>% mutate(reason = "entries had HTML contents in sitemap and have been filtered"),
  filtered_global_step_6_excluded_sitemaps_df %>% mutate(reason = "entries had other non related content"),
  missing_sitemap_url        %>% mutate(reason = "entries had missing sitemap_URL and have been removed"),
  missing_sitemap_content    %>% mutate(reason = "entries had missing sitemap_content and have been removed")
) %>%
  transmute(
    type = "sitemap",
    domain = domain_url,
    link = sitemap_URL,
    reason = reason
  ) %>%
  bind_rows(
    
    filtered_dynamic_sitemaps_df %>%
      mutate(reason = "entries were filtered as dynamic websites") %>%
      transmute(
        type = "domain",
        domain = domain_url,
        link = domain_url,
        reason = reason
      )
  )

write.csv(p1_excluded_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_excluded_sitemaps.csv", row.names = FALSE)

# Summary 
print(paste(nrow(p1_all_sitemaps), "total entries exported to: p1_all_sitemaps"))
print(paste(nrow(sitemap_scraper_clean_sitemaps), "clean entries exported to: sitemap_scraper_clean_sitemaps"))
print(paste(nrow(p1_excluded_sitemaps), "excluded entries exported to: p1_excluded_sitemaps"))


```

## Code Chunk: Step 7 – Generation of Summary Report and Debug Diagnostics

### Summary:
This step synthesizes the results of all previous stages into a structured diagnostic and reporting output. It compiles success rates, failure points, and per-step metrics into a final summary table. Additionally, debug data from multiple steps is harmonized and exported to facilitate transparency and reproducibility. The final report is saved and rendered in PDF format using R Markdown.

**Inputs:**  
- All intermediate data frames and debug outputs from steps 1 through 6, especially `step_1_domain_urls_robotsUrls_df`, `step_2_domain_Urls_robotsUrls_robotsContents_df`, `step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df`, `step_4_1_missing_sitemaps_df`, `step_5_valid_sitemaps_check`, and `step_6_cleaned_df`.

**Outputs:**  
- A markdown-style report string (`step_7_report_content`) summarizing each processing stage.
- A PDF report generated via `rmarkdown::render()`.
- A debug CSV file `p1_debug_sitemap_data.csv` with harmonized entries from all error-producing stages.

#### Function: `step_7_generate_final_report`
This function constructs a comprehensive overview of the pipeline’s performance. It first assembles a summary table with counts of total, successful, and partially successful operations per step. It then defines and applies a helper function (`format_debug_df`) to standardize various debug data frames into a common schema. All debug logs are merged into one file for external inspection. Finally, a text-based R Markdown report is created and rendered to PDF, capturing high-level outcomes and domain-level sitemap availability statistics. This function ensures replicability, auditability, and interpretability of the scraping process.

```{r Step 7 }
step_7_generate_final_report <- function() {
  # Create overall summary table
  step_7_overall_summary <- data.frame(
    Step = c(
      "Step 1: Robots.txt URLs Retrieval",
      "Step 2: Robots.txt Contents Retrieval",
      "Step 3: Sitemap URLs Extraction from Robots.txt",
      "Step 4: Typical Sitemap URLs Retrieval",
      "Step 5: Sitemap Contents Retrieval",
      "Step 6: Final Data"
    ),
    Total_Items = c(
      nrow(global_input_all_domains),
      nrow(step_1_domain_urls_robotsUrls_df),
      nrow(step_2_domain_Urls_robotsUrls_robotsContents_df),
      nrow(if (exists("step_4_1_missing_sitemaps_df")) step_4_1_missing_sitemaps_df else data.frame()),
      nrow(if (exists("step_5_valid_sitemaps_check")) step_5_valid_sitemaps_check else data.frame()),
      nrow(step_6_cleaned_df)
    ),
    Successful = c(
      sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt)),
      sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)),
      sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check != "no sitemap"),
      sum(if (exists("step_4_1_missing_sitemaps_df")) !is.na(step_4_1_missing_sitemaps_df$sitemap_URL) else 0),
      sum(if (exists("step_5_valid_sitemaps_check")) !is.na(step_5_valid_sitemaps_check$sitemap_content) else 0),
      sum(!is.na(step_6_cleaned_df$sitemapUrls))
    ),
    Partially_Successful = c(
      sum(is.na(step_1_domain_urls_robotsUrls_df$robots_txt)),
      sum(is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)),
      sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check == "no sitemap"),
      sum(if (exists("step_4_1_missing_sitemaps_df")) is.na(step_4_1_missing_sitemaps_df$sitemap_URL) else 0),
      sum(if (exists("step_5_valid_sitemaps_check")) is.na(step_5_valid_sitemaps_check$sitemap_content) else 0),
      sum(is.na(step_6_cleaned_df$sitemapUrls))
    )
  )

  # Standardize and combine debug DataFrames
  format_debug_df <- function(df, step_name) {
    if (!is.null(df) && nrow(df) > 0) {
      # Define a standard column structure
      standard_columns <- c("Step", "domain_url", "robots_txt", "sitemap_URL", "issue", "note")
      
      # Ensure all required columns exist
      df <- df %>%
        mutate(
          Step = step_name,
          domain_url = if (!"domain_url" %in% colnames(df)) NA else domain_url,
          robots_txt = if (!"robots_txt" %in% colnames(df)) NA else robots_txt,
          sitemap_URL = if (!"sitemap_URL" %in% colnames(df)) NA else sitemap_URL,
          issue = if (!"issue" %in% colnames(df)) NA else issue,
          note = if (!"note" %in% colnames(df)) NA else note
        )
      
      # Reorder columns to match the standard structure
      df <- df[, standard_columns]
      return(df)
    }
    return(NULL)
  }

  # Format all debug DataFrames
  debug_dfs <- list(
    if (exists("step_1_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_1_1_debug_unsuccsesful_fetches_df, "Step 1"),
    if (exists("step_2_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_2_1_debug_unsuccsesful_fetches_df, "Step 2"),
    if (exists("step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df")) format_debug_df(
      step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
        filter(sitemap_check == "no sitemap") %>%
        mutate(issue = "No sitemap URL"),
      "Step 3"
    ),
    if (exists("step_4_1_missing_sitemaps_df")) format_debug_df(
      step_4_1_missing_sitemaps_df %>%
        filter(is.na(sitemap_URL)) %>%
        mutate(issue = "No typical sitemap URL found"),
      "Step 4"
    ),
    if (exists("step_5_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_5_1_debug_unsuccsesful_fetches_df, "Step 5")
  )

  # Combine all debug DataFrames
  step_7_debug_data <- do.call(rbind, Filter(Negate(is.null), debug_dfs))

  # Save debug data if available
  if (!is.null(step_7_debug_data) && nrow(step_7_debug_data) > 0) {
    write.csv(step_7_debug_data,"/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_debug_sitemap_data.csv", row.names = FALSE)
  }


# Generate Markdown report content with "X of Y" formatting
# Generate Markdown report content with "X of Y" formatting
step_7_report_content <- c(
  "# Final Report",
  "## Overall Summary",
  knitr::kable(step_7_overall_summary, format = "markdown"),
  "## Detailed Metrics",
  paste("### Step 1:", paste(sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt)), "of", nrow(step_1_domain_urls_robotsUrls_df), "robots.txt URLs retrieved")),
  paste("### Step 2:", paste(sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)), "of", nrow(step_2_domain_Urls_robotsUrls_robotsContents_df), "robots.txt contents retrieved")),
  paste("### Step 3:", paste(sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check != "no sitemap"), "of", nrow(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df), "sitemap URLs extracted")),
  paste("### Step 4:", paste(sum(!is.na(step_4_1_missing_sitemaps_df$sitemap_URL)), "of", nrow(step_4_1_missing_sitemaps_df), "typical sitemap URLs found")),
  paste("### Step 5:", paste(sum(!is.na(step_5_valid_sitemaps_check$sitemap_content)), "of", nrow(step_5_valid_sitemaps_check), "sitemap contents retrieved")),
  paste("### Step 6: Final dataset includes", paste(nrow(step_6_cleaned_df), "of", nrow(step_6_cleaned_df), "domains")),

  # --- New: Domain summary statistics ---
  "## Domain-Level Summary",
  paste("### Input domains:", length(unique(global_input_all_domains$domain_url))),
  paste("### Domains with valid sitemaps:", length(unique(step_6_cleaned_df$domain_url))),
  paste("### Domains without sitemaps:", 
        length(setdiff(unique(global_input_all_domains$domain_url), unique(step_6_cleaned_df$domain_url))))
)

# Save and render report
step_7_report_path <- "/Users/zorbeyozcan/newsmedia_scraper/documentation/sitema_scraper_report"
writeLines(step_7_report_content, step_7_report_path)
rmarkdown::render(step_7_report_path, output_format = "pdf_document")

print("Final report and debug file created successfully.")
  
}

# Execute the final report generation function
step_7_generate_final_report()

```

## Code Chunk: Step 8 – Environment Cleanup and Memory Optimization

### Summary:
This final step ensures that the R environment is cleared of all intermediate objects, functions, and temporary data structures that are no longer needed after the successful execution of the pipeline. This cleanup enhances reproducibility by isolating output artifacts and reduces memory usage for subsequent computations or session reuse.

**Inputs:**  
- No external data is required. The operation targets the internal R environment and variables generated in prior steps.

**Outputs:**  
- All temporary variables, helper functions, and debug frames related to steps 5–7 are deleted.  
- Any remaining objects with names matching the pattern `^step_` are also purged via regular expression matching.  
- The environment is left in a minimal, export-only state, preserving only final results and exported files.

This operation is essential in replication-oriented workflows where deterministic output and minimal side effects are prerequisites for robustness and transparency.

```{r Step 8 , warning=FALSE}

# Step 1 cleanup
rm(
  input_df, 
  step_1_all_df, 
  step_1_debug_df, 
  step_1_clean_df, 
  step_1_get_namespace_type_func, 
  step_1_get_root_tag_func, 
  step_1_get_sitemap_type_func
)

# Step 2 cleanup
rm(
  step_2_get_root_tag_func, 
  step_2_follow_path_func, 
  step_2_process_sitemap_func, 
  step_2_all_df, 
  step_2_clean_df, 
  step_2_debug_df, 
  total_rows
)

# Step 4 cleanup
rm(step_3_clean_df)

# Step 4 cleanup
rm(
  sitemap_inspector_debug_df, 
  step_4_wrangling_df, 
  export_labeled_sitemaps, 
  export_no_index_sitemap,
  summary_table_sitemap,
  domains_index,
  num_domains_with_index,
  num_domains_no_index,
  export_simplified_labeled_sitemaps_df, 
  desired_order, 
  other_cols
)

# Step 5 cleanup
rm(step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents, 
   step_5_1_debug_unsuccsesful_fetches_df, step_5_get_sitemap_content_func, 
   step_5_valid_sitemaps_check, step_5_total_valid_sitemaps_check, 
   step_5_loaded_valid_sitemaps_check, domains_with_successful_sitemaps)

# Step 6 cleanup (Keep only the four export data frames)
rm(step_6_cleaned_df, step_6_cleaned_df_fast, step_6_output_path, 
   filtered_media_sitemaps_df, filtered_global_excluded_sitemaps_df, filtered_irrelevant_sitemaps_df,
   filtered_html_sitemaps_df, filtered_global_step_6_excluded_sitemaps_df,
   filtered_dynamic_sitemaps_df, missing_sitemap_url, missing_sitemap_content, 
   failed_sitemaps, all_sitemap_data, export_broken_sitemaps, excluded_domains_df)

# Step 7 cleanup
rm(step_7_overall_summary, step_7_debug_data, step_7_generate_final_report, 
   step_7_report_path, step_7_report_content, debug_dfs, format_debug_df)

# Remove any remaining functions or variables that were not explicitly removed
rm(list = ls(pattern = "^step_"))

print("All functions, values, and data frames have been removed successfully.")

```



