---
title: "sitemap_scraper"
author: "Zorbey Özcan"
date: "2025-05-24"
output: html_document
---

# What does this code do? 

This code generates data and produces the final prodcut of phase 1 of the NewsMedia data collection process. 

It takes a list of news media domain names, that are integrated into the paberboy r package by @JBGruber. 
It returns data containing all publicly available sitemaps of those domain names. 

## The data includes:

A data.frame with the columns: 

---

|          | domain_urls | robots_urls | robots_contents | sitemap_urls | sitemap_contents | sitemap_check |
|----------|----------|----------|----------|----------|----------|----------|
| **1** | the url of the domain  | the url of the robots.txt file  | the contents of the robots.txt file  | the url of the sitemap.xml file | the contents of the sitemap.xml file  | a check or comment for that entry  |


## Limitations: 

In this project, I only focus on scraping German news media articles. For that reason, the list contains only German news media publications. 
- Not all sitemaps are available 


```{r Preparation}
# knitting Options 
knitr::opts_chunk$set(
  echo    = TRUE,       
  results = 'hide',  
  message = FALSE,  
  warning = FALSE    
)
library(httr)
library(dplyr)
library(tidyr)
library(rmarkdown)
library(rvest)
```


```{r Retrieving input data }
# Define the GitHub URL
step_0_url <- "https://github.com/JBGruber/paperboy"

# Read the HTML content of the page
step_0_page <- read_html(step_0_url)

# Extract all tables from the HTML
step_0_tables_list <- step_0_page %>% html_elements("table")

# Convert the sixth table to a data frame
global_input_all_domains <- step_0_tables_list[[6]] %>% html_table()

# Filter rows where the domain column contains ".de", "postillion", or "finanzen" for all german newsmedia
global_input_all_domains <- global_input_all_domains %>%
  filter(grepl("\\.de|postillion|finanzen|faz", domain, ignore.case = TRUE)) %>%
  select(domain_url = domain)

# Correct the domain entry with a duplicated ".de"
global_input_all_domains <- global_input_all_domains %>%
  mutate(domain_url = ifelse(domain_url == "abendzeitung-muenchen.de.de", 
                             "abendzeitung-muenchen.de", 
                             domain_url))

```

# Step 1:
## This code chunk takes the global_input_all_domains and searches for robots.txt urls for all those domains. It returns step_1_domain_urls_robotsUrls_df and passes it to the next chunk.
### This code produces traffic. 
```{r Step 1 }
# Function to retrieve robots.txt URL from a domain using different protocols
step_1_robots_url_func <- function(step_1_domain_url) {
  # Construct possible robots.txt URLs for HTTP, HTTPS, and HTTPS with www
  step_1_robots_http_url <- paste0("http://", step_1_domain_url, "/robots.txt")
  step_1_robots_https_url <- paste0("https://", step_1_domain_url, "/robots.txt")
  step_1_robots_www_https_url <- paste0("https://www.", step_1_domain_url, "/robots.txt")

  # Initialize variables to store responses
  step_1_response_http <- NULL
  step_1_response_https <- NULL
  step_1_response_www_https <- NULL

  # Attempt to fetch the robots.txt file using HTTP
  step_1_response_http <- tryCatch(
    {
      httr::HEAD(step_1_robots_http_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Attempt to fetch the robots.txt file using HTTPS
  step_1_response_https <- tryCatch(
    {
      httr::HEAD(step_1_robots_https_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Attempt to fetch the robots.txt file using HTTPS with www
  step_1_response_www_https <- tryCatch(
    {
      httr::HEAD(step_1_robots_www_https_url, followlocation = TRUE)
    },
    error = function(e) NULL
  )

  # Check and return the first valid robots.txt URL found
  if (!is.null(step_1_response_http) && step_1_response_http$status_code == 200) {
    print(paste("Returning HTTP robots.txt URL:", step_1_robots_http_url))
    return(step_1_robots_http_url)
  } else if (!is.null(step_1_response_https) && step_1_response_https$status_code == 200) {
    print(paste("Returning HTTPS robots.txt URL:", step_1_robots_https_url))
    return(step_1_robots_https_url)
  } else if (!is.null(step_1_response_www_https) && step_1_response_www_https$status_code == 200) {
    print(paste("Returning HTTPS www robots.txt URL:", step_1_robots_www_https_url))
    return(step_1_robots_www_https_url)
  } else {
    print("No valid robots.txt URL found. Returning NA.")
    return(NA)
  }
}

# Vectorize the function for processing multiple domains
step_1_get_robots_url_func <- Vectorize(step_1_robots_url_func)

# Create a new DataFrame for storing robots.txt URLs
step_1_domain_urls_robotsUrls_df <- global_input_all_domains

# Add a new column with robots.txt URLs using the vectorized function
step_1_domain_urls_robotsUrls_df$robots_txt <- step_1_get_robots_url_func(step_1_domain_urls_robotsUrls_df$domain_url)

# Count the total number of domains and valid robots.txt URLs
step_1_total_domains_check <- nrow(step_1_domain_urls_robotsUrls_df)
step_1_valid_robots_check <- sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt))

# Print the summary of the robots.txt retrieval
if (step_1_valid_robots_check == step_1_total_domains_check) {
  print(paste(step_1_valid_robots_check, "of", step_1_total_domains_check, "robots.txt URLs found"))
} else {
  print(paste(step_1_valid_robots_check, "of", step_1_total_domains_check, "robots.txt URLs found. Some are missing."))
}

# Debug function to create a DataFrame for unsuccessful robots.txt fetches
if (step_1_valid_robots_check != step_1_total_domains_check) {
  # Create a debug DataFrame with domains where robots.txt was not found
  step_1_1_debug_unsuccsesful_fetches_df <- step_1_domain_urls_robotsUrls_df %>%
    filter(is.na(robots_txt)) %>%  # Filter rows where robots.txt is NA
    select(domain_url, robots_txt)  # Include relevant columns for debugging

  # Add a column to indicate that no robots.txt was found
  step_1_1_debug_unsuccsesful_fetches_df <- step_1_1_debug_unsuccsesful_fetches_df %>%
    mutate(
      issue = "No valid robots.txt URL found"
    )

  # Print confirmation
  print(paste("Created step_1_1_debug_unsuccsesful_fetches_df with", nrow(step_1_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}


```

# Step 2:
## This code chunk takes the  and . It returns   with    .
### This code produces traffic. 
```{r Step 2 }
# Function to retrieve the content of a robots.txt file given its URL
step_2_robots_txt_content_func <- function(step_2_url) {
  # Check the HTTP status of the URL
  step_2_response <- tryCatch(
    {
      httr::HEAD(step_2_url, timeout(5))  # Check the HEAD response for the URL
    },
    error = function(e) NULL
  )

  # Debugging: Print the HTTP status or connection error
  if (!is.null(step_2_response)) {
    print(paste("HTTP status for", step_2_url, ":", step_2_response$status_code))
    if (step_2_response$status_code == 200) {
      print(paste("robots.txt successfully found for:", step_2_url))
    }
  } else {
    print(paste("Error: Unable to connect to", step_2_url))
  }

  # Fetch and return the content of the robots.txt file if accessible
  tryCatch(
    {
      httr::GET(step_2_url) %>% content("text", encoding = "UTF-8")  # Get the full content
    },
    error = function(e) NA  # Return NA if any error occurs
  )
}

# Apply the function to each URL and store the results in a new DataFrame
step_2_domain_Urls_robotsUrls_robotsContents_df <- step_1_domain_urls_robotsUrls_df %>%
  mutate(
    robots_txt_content = sapply(robots_txt, step_2_robots_txt_content_func)
  )

# Calculate the total number of domains and valid robots.txt content entries
step_2_total_domains_check <- nrow(step_1_domain_urls_robotsUrls_df)
step_2_valid_contents_check <- sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content))

# Print the summary of the robots.txt content retrieval
if (step_2_valid_contents_check == step_2_total_domains_check) {
  print(paste(step_2_valid_contents_check, "of", step_2_total_domains_check, "robots.txt contents successfully fetched"))
} else {
  print(paste(step_2_valid_contents_check, "of", step_2_total_domains_check, "robots.txt contents fetched. Some are missing."))
}

# Debug function to create a DataFrame for unsuccessful robots.txt content fetches
if (step_2_valid_contents_check != step_2_total_domains_check) {
  # Create a debug DataFrame with domains where robots.txt content was not successfully fetched
  step_2_1_debug_unsuccsesful_fetches_df <- step_2_domain_Urls_robotsUrls_robotsContents_df %>%
    filter(is.na(robots_txt_content)) %>%  # Filter rows where robots.txt content is NA
    mutate(
      http_status = sapply(robots_txt, function(url) {
        response <- tryCatch(
          {
            httr::HEAD(url, timeout(5))
          },
          error = function(e) NULL
        )
        if (!is.null(response)) {
          return(response$status_code)  # Return the HTTP status code if available
        } else {
          return("Error")  # Indicate an error if no response
        }
      }),
      issue = "robots.txt content not fetched"  # Indicate the issue
    ) %>%
    select(domain_url, robots_txt, http_status, issue)  # Include relevant columns for debugging

  # Print confirmation
  print(paste("Created step_2_1_debug_unsuccsesful_fetches_df with", nrow(step_2_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}

```



# Step 3:
## This code chunk takes the  and . It returns   with    .
### This code runs locally. 
```{r Step 3 }
# Function to extract sitemap URLs from robots.txt content
step_3_extract_sitemap_urls_func <- function(step_3_content) {
  # Remove line breaks and replace with spaces
  step_3_clean_content <- gsub("[\r\n]+", " ", step_3_content)

  # Regular expression to identify sitemap URLs, case-insensitive
  step_3_sitemap_pattern <- "(?i)sitemap:\\s*(https?://[\\w./~:-]+)"

  # Extract all matching URLs
  step_3_sitemaps <- regmatches(step_3_clean_content, gregexpr(step_3_sitemap_pattern, step_3_clean_content, perl = TRUE))[[1]]

  # Remove the "sitemap:" prefix from results
  step_3_sitemaps <- gsub("(?i)sitemap[:\\s]+", "", step_3_sitemaps, perl = TRUE)

  # Return unique URLs or NA if none found
  if (length(step_3_sitemaps) == 0) {
    return(NA)
  } else {
    return(unique(step_3_sitemaps))
  }
}

# Expand the DataFrame by adding sitemap URLs and related information
step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df <- step_2_domain_Urls_robotsUrls_robotsContents_df %>%
  mutate(
    sitemap_URLs = lapply(robots_txt_content, function(step_3_content) {
      if (is.na(step_3_content)) {
        return(NA)  # Return NA if no robots.txt content is available
      } else {
        return(step_3_extract_sitemap_urls_func(step_3_content))  # Extract sitemap URLs
      }
    }),
    sitemap_check = case_when(
      is.na(sitemap_URLs) ~ "no sitemap",                          # No sitemaps found
      lengths(sitemap_URLs) == 1 ~ "one sitemap",                  # One sitemap found
      lengths(sitemap_URLs) > 1 ~ "multiple sitemaps"              # Multiple sitemaps found
    )
  ) %>%
  tidyr::unnest(sitemap_URLs, keep_empty = TRUE) %>%  # Flatten lists and keep empty entries
  rename(sitemap_URL = sitemap_URLs)  # Rename the column for clarity

# Calculate the total number of sitemap URLs and domains with/without sitemaps
step_3_total_sitemaps_check <- sum(!is.na(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_URL))
step_3_domains_with_sitemaps_check <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check != "no sitemap") %>%
  distinct(domain_url) %>%
  nrow()
step_3_domains_without_sitemaps_check <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check == "no sitemap") %>%
  distinct(domain_url) %>%
  nrow()

# Print the summary of sitemap extraction
print(paste("Total sitemap URLs found:", step_3_total_sitemaps_check))
print(paste("Unique domains with sitemap URLs:", step_3_domains_with_sitemaps_check))
print(paste("Unique domains without sitemap URLs:", step_3_domains_without_sitemaps_check))

```


# Step 4:
## This code chunk takes the  and . It returns   with    .
### This code produces traffic.
```{r Step 4 }
# Define typical sitemap paths
step_4_typical_sitemap_paths_vec <- c(
  "/sitemap.xml", "/sitemap_index.xml", "/sitemap-index.xml", "/sitemaps/sitemap.xml",
  "/sitemaps/sitemap_index.xml", "/sitemap-posts.xml", "/sitemap-pages.xml",
  "/sitemap-products.xml", "/sitemap-2025-01.xml", "/sitemap-2024.xml",
  "/sitemap-images.xml", "/sitemap-videos.xml", "/sitemap-en.xml",
  "/sitemap-de.xml", "/sitemap.php", "/sitemap.txt", "/sitemap.xml.gz",
  "/sitemap/", "/sitemapindex.xml", "/sitemap/index.xml", "/sitemap1.xml",
  "/~/sitemap.xml", "/~/sitemap_index.xml", "/~/sitemap-index.xml",
  "/~/sitemaps/sitemap.xml", "/~/sitemaps/sitemap_index.xml", "/~/sitemap-posts.xml",
  "/~/sitemap-pages.xml", "/~/sitemap-products.xml", "/~/sitemap-2025-01.xml",
  "/~/sitemap-2024.xml", "/~/sitemap-images.xml", "/~/sitemap-videos.xml",
  "/~/sitemap-en.xml", "/~/sitemap-de.xml", "/~/sitemap.php", "/~/sitemap.txt",
  "/~/sitemap.xml.gz", "/~/sitemap/", "/~/sitemapindex.xml", "/~/sitemap/index.xml",
  "/~/sitemap1.xml"
)

# Function to check typical sitemap URLs for a given domain
step_4_find_typical_sitemaps_func <- function(step_4_domain) {
  step_4_valid_sitemaps <- c()  # List to store found sitemaps

  for (step_4_path in step_4_typical_sitemap_paths_vec) {
    step_4_url <- paste0("https://", step_4_domain, step_4_path)  # Construct full URL
    step_4_response <- tryCatch(
      {
        httr::HEAD(step_4_url, timeout(5))  # HTTP HEAD request
      },
      error = function(e) NULL
    )

    if (!is.null(step_4_response)) {
      # Print HTTP status for debugging
      print(paste("HTTP status for", step_4_url, ":", step_4_response$status_code))

      # Check if the sitemap is valid (status code 200)
      if (step_4_response$status_code == 200) {
        print(paste("Valid sitemap found for domain", step_4_domain, ":", step_4_url))
        step_4_valid_sitemaps <- c(step_4_valid_sitemaps, step_4_url)
      }
    } else {
      print(paste("Error: Unable to connect to", step_4_url))
    }
  }

  return(step_4_valid_sitemaps)  # Return all found sitemaps
}

# Create a new DataFrame for domains with no sitemaps
step_4_1_missing_sitemaps_df <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  filter(sitemap_check == "no sitemap") %>%
  distinct(domain_url) %>%
  mutate(
    sitemap_URL = NA,            # Add column for found sitemaps
    sitemap_check = "no sitemap" # Initial status
  )

# Search for typical sitemaps and update the DataFrame
step_4_1_missing_sitemaps_df <- step_4_1_missing_sitemaps_df %>%
  rowwise() %>%
  mutate(
    found_sitemaps = list(step_4_find_typical_sitemaps_func(domain_url))  # Find typical sitemaps
  ) %>%
  tidyr::unnest(found_sitemaps, keep_empty = TRUE) %>%
  mutate(
    sitemap_URL = ifelse(is.na(found_sitemaps), NA, found_sitemaps),  # Add found sitemaps
    sitemap_check = ifelse(is.na(found_sitemaps), "no sitemap", "found typical sitemap")
  ) %>%
  select(domain_url, sitemap_URL, sitemap_check)  # Keep relevant columns

# Merge original and new results into the final DataFrame
step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df <- step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
  left_join(
    step_4_1_missing_sitemaps_df %>%
      filter(!is.na(sitemap_URL)),  # Only include new sitemaps
    by = "domain_url",
    suffix = c("", "_new")
  ) %>%
  mutate(
    sitemap_URL = coalesce(sitemap_URL_new, sitemap_URL),          # Merge URLs
    sitemap_check = coalesce(sitemap_check_new, sitemap_check)    # Merge status
  ) %>%
  select(-ends_with("_new"))  # Remove helper columns

# Check: Print results for validation
step_4_total_domains_check <- nrow(step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df)
step_4_total_sitemaps_check <- sum(!is.na(step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df$sitemap_URL))
step_4_domains_with_sitemaps_check <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  filter(!is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()
step_4_domains_without_sitemaps_check <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  filter(is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()
step_4_new_sitemaps_added_check <- step_4_1_missing_sitemaps_df %>%
  filter(!is.na(sitemap_URL)) %>%
  distinct(domain_url) %>%
  nrow()

print(paste("Total sitemap URLs found:", step_4_total_sitemaps_check))
print(paste("Unique domains with sitemap URLs:", step_4_domains_with_sitemaps_check))
print(paste("Unique domains without sitemap URLs:", step_4_domains_without_sitemaps_check))
print(paste("This step added", step_4_new_sitemaps_added_check, "sitemap URLs"))

```

# Step 5:
## This code chunk takes the  and . It returns   with    .
### This code produces traffic. 
```{r Step 5 }
# Function to fetch the content of a sitemap URL and capture the HTTP status or errors
step_5_get_sitemap_content_func <- function(step_5_url) {
  if (is.na(step_5_url)) {
    print("Sitemap URL is NA, skipping...")
    return(list(content = NA, status = "NA"))  # Return NA for content and status
  }

  step_5_result <- tryCatch(
    {
      step_5_response <- httr::GET(step_5_url, timeout(120))  # HTTP GET request with timeout
      print(paste("Fetching sitemap for URL:", step_5_url, "Status code:", step_5_response$status_code))
      
      if (step_5_response$status_code == 200) {
        # Check if the URL points to a .gz file
        if (grepl("\\.gz$", step_5_url, ignore.case = TRUE)) {
          print("Detected .gz sitemap, attempting to decompress...")

          # Retrieve raw binary content
          raw_content <- httr::content(step_5_response, as = "raw")  
          
          # Decompress the .gz content using gzcon()
          con <- gzcon(rawConnection(raw_content))
          xml_text <- readLines(con, warn = FALSE)
          close(con)
          
          # Return the extracted XML content
          list(content = paste(xml_text, collapse = "\n"), status = step_5_response$status_code)
          
        } else {
          # Standard handling for non-gzipped sitemaps
          list(content = httr::content(step_5_response, "text", encoding = "UTF-8"), status = step_5_response$status_code)
        }
        
      } else {
        print(paste("Failed to fetch sitemap for URL:", step_5_url, "Status code:", step_5_response$status_code))
        list(content = NA, status = step_5_response$status_code)
      }
    },
    error = function(e) {
      print(paste("Error fetching sitemap for URL:", step_5_url))
      list(content = NA, status = "Error")  # Capture error as status
    }
  )

  return(step_5_result)
}

# Copy the DataFrame and add columns for sitemap content and status
step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents <- step_4_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_sitemapUrlsWeb_df %>%
  mutate(
    result = lapply(sitemap_URL, step_5_get_sitemap_content_func),  # Fetch the content and status
    sitemap_content = sapply(result, function(x) x$content),        # Extract content
    http_status = sapply(result, function(x) x$status)             # Extract HTTP status or error
  ) %>%
  select(-result)  # Remove the intermediate result column

# Check: Only consider rows with a valid sitemap_URL
step_5_valid_sitemaps_check <- step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents %>%
  filter(!is.na(sitemap_URL))

step_5_total_valid_sitemaps_check <- nrow(step_5_valid_sitemaps_check)
step_5_loaded_valid_sitemaps_check <- sum(!is.na(step_5_valid_sitemaps_check$sitemap_content))

print(paste("Total sitemap URLs with valid links:", step_5_total_valid_sitemaps_check))
print(paste(step_5_loaded_valid_sitemaps_check, "of", step_5_total_valid_sitemaps_check, "sitemaps were loaded successfully"))

# If not all valid sitemaps were fetched successfully, create a debug DataFrame
if (step_5_loaded_valid_sitemaps_check != step_5_total_valid_sitemaps_check) {
  # Identify domains with at least one successfully fetched sitemap
  domains_with_successful_sitemaps <- step_5_valid_sitemaps_check %>%
    filter(!is.na(sitemap_content)) %>%
    pull(domain_url)
  
  # Create the debug DataFrame
  step_5_1_debug_unsuccsesful_fetches_df <- step_5_valid_sitemaps_check %>%
    filter(is.na(sitemap_content)) %>%
    mutate(
      is_only_sitemap = !domain_url %in% domains_with_successful_sitemaps  # Check if this is the only sitemap for the domain
    ) %>%
    select(domain_url, sitemap_URL, http_status, is_only_sitemap)  # Include status and exclusivity in debug

  print(paste("Created step_5_1_debug_unsuccsesful_fetches_df with", nrow(step_5_1_debug_unsuccsesful_fetches_df), "unsuccessful fetches"))
}

```


# Step 6:
## This code chunk takes the  and . It returns   with    .
### This code runs locally. 
```{r Step 6 }
# Step 6: Clean and export final sitemap dataset
step_6_cleaned_df <- step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents

# Assign a unique domainID to each unique domain
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(domainID = as.numeric(factor(domain_url)))  # Each unique domain gets a unique ID

# Step 6.1 - Filter Media Sitemaps - These contain links to pictures, videos and podcasts exclusively
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl(paste(c("image","bilder", "picture", "fotografie", "photo", "foto", "imagegallery", "gallery", "video", "media", "audio", "podcasts", "podcast" ), collapse = "|"), sitemap_URL, ignore.case = TRUE), "media_sitemaps", NA))

filtered_media_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_media_sitemaps_df), "entries had media-related sitemaps and have been filtered"))

# Step 6.2 - Filter other unrelevant sitemaps 
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl(paste(c( "themen.*-az", # these contain topics and not articles
                                                  "author",      # these contain author pages and not articles
                                                  "sport",       # these contain sports and live broacasts and not articles
                                                  "shop",        # these contain shop elements and not articles
                                                  "security"),   # these contain administrative sitemaps and not articles
                                                  collapse = "|"), sitemap_URL, ignore.case = TRUE),
                                                  "irrelevant_sitemaps", NA))

filtered_irrelevant_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_irrelevant_sitemaps_df), "entries had other non related sitemaps and have been filtered"))


# Step 6.3 - Filter HTML Contents
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(grepl("<!DOCTYPE html", sitemap_content, ignore.case = TRUE), "html contents", NA))

filtered_html_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_html_sitemaps_df), "entries had HTML contents in sitemap and have been filtered"))

# Step 6.4 - Filter Dynamic Websites which do not rely on sitemaps 
# (I verified those as dynamic websites manually by disabeling java script in my browser and using the free browser plug in "Wappalyzer")
# (Other domains are TV or radio channels, which carry TV Shows and podcasts, but not articles) 
blocked_domains <- c(
  "dnn.de", "express.de", "focus.de", "haz.de", "ksta.de", "lvz.de",
  "maz-online.de", "ostsee-zeitung.de", "rbb24.de", "rnd.de",
  "ruhrnachrichten.de", "saechsische.de", 
  # tv channels and radio:
  "deutschlandfunk.de","deutschlandfunkkultur.de", "kabeleins.de", "prosieben.de", "vox.de"
)

step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(domain_url %in% blocked_domains, "dynamic websites", NA))

filtered_dynamic_sitemaps_df <- step_6_cleaned_df %>% filter(!is.na(filtered_because))
step_6_cleaned_df <- step_6_cleaned_df %>% filter(is.na(filtered_because)) %>% select(-filtered_because)
print(paste(nrow(filtered_dynamic_sitemaps_df), "entries were filtered as dynamic websites"))

# Step 6.5 - Filter Global Excluded Sitemaps (manually verified non-article sources)
# These are structurally valid but contain only keywords, finance data, cities or technical indexes.
excluded_sitemaps <- c(
  "https://www.nw.de/_retresco/sitemap/index.xml",                   # this sitemap contains topics and not articles
  "https://www.presseportal.de/sitemap-de-index-keywords.xml",       # this sitemap contains keywords and not articles
  "https://www.presseportal.de/sitemap-de-index-newsrooms.xml",      # this sitemap contains advertisements and not articles
  "https://www.presseportal.de/sitemap-de-index-cities.xml",         # this sitemap contains topics by region and not articles
  "https://www.tag24.de/sitemap_tag24_d.xml",                        # this sitemap contains deleted articles 
  "https://www.finanzen.net/sitemap/sitemap.xml",                    # this sitemap contains financial news tickers and not articles
  "https://www.finanzen.net/xml/google-sitemaps/google_sitemap.xml", # this sitemap contains financial news tickers and not articles
  "https://www.finanzen.net/ratgeber/sitemap_index.xml"              # this sitemap contains financial news tickers and not articles
)

# Filter entries matching the global exclusion list
step_6_cleaned_df <- step_6_cleaned_df %>%
  mutate(filtered_because = ifelse(sitemap_URL %in% excluded_sitemaps, "excluded_sitemaps", NA))

# Create filtered DataFrame
filtered_global_step_6_excluded_sitemaps_df <- step_6_cleaned_df %>%
  filter(!is.na(filtered_because))

# Remove excluded entries from the main DataFrame
step_6_cleaned_df <- step_6_cleaned_df %>%
  filter(is.na(filtered_because)) %>%
  select(-filtered_because)

# Output summary
print(paste(nrow(filtered_global_step_6_excluded_sitemaps_df), "entries had other non related content"))

# Remove entries with missing sitemap_URL and create missing_sitemap_url df
missing_sitemap_url <- step_6_cleaned_df %>% filter(is.na(sitemap_URL)) %>% mutate(filtered_because = "missing sitemap URL")
step_6_cleaned_df <- step_6_cleaned_df %>% filter(!is.na(sitemap_URL))
print(paste(nrow(missing_sitemap_url), "entries had missing sitemap_URL and have been removed"))

# Remove entries with missing sitemap_content and create missing_sitemap_content df
missing_sitemap_content <- step_6_cleaned_df %>% filter(is.na(sitemap_content)) %>% mutate(filtered_because = "missing sitemap content")
step_6_cleaned_df <- step_6_cleaned_df %>% filter(!is.na(sitemap_content))
print(paste(nrow(missing_sitemap_content), "entries had missing sitemap_content and have been removed"))

# Combine missing_sitemap_url and missing_sitemap_content into failed_sitemaps
failed_sitemaps <- bind_rows(missing_sitemap_url, missing_sitemap_content)
print(paste(nrow(failed_sitemaps), "entries are in the failed_sitemaps dataset"))

# Combine all filtered datasets into export_broken_sitemaps
export_broken_sitemaps <- bind_rows(
  filtered_media_sitemaps_df, 
  filtered_html_sitemaps_df, 
  filtered_dynamic_sitemaps_df,
  failed_sitemaps
)

# Adjusting sitemap_check
step_6_cleaned_df <- step_6_cleaned_df %>%
  group_by(domain_url) %>%
  mutate(sitemap_check = ifelse(n() == 1, "one sitemap", "multiple sitemaps")) %>%
  ungroup()

### Exporting all data:

# p1 all sitemaps: 
p1_all_sitemaps <- bind_rows(step_6_cleaned_df, export_broken_sitemaps)
write.csv(p1_all_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_all_sitemaps.csv", row.names = FALSE)

# p1 clean sitemaps: 
sitemap_scraper_clean_sitemaps <- step_6_cleaned_df %>%
  transmute(
    domain_id = as.numeric(factor(domain_url)),         
    domain_url = domain_url,
    layer_1_url = sitemap_URL
  ) %>%
  mutate(layer_1_url_id = row_number()) %>%            
  select(domain_id, domain_url, layer_1_url_id, layer_1_url)
write.csv(sitemap_scraper_clean_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/data/sitemap_scraper_clean_sitemaps.csv", row.names = FALSE) 


# p1 excluded sitemaps:
p1_excluded_sitemaps <- bind_rows(
  
  filtered_media_sitemaps_df  %>% mutate(reason = "media sitemap - images, videos, podcasts"),
  filtered_irrelevant_sitemaps_df %>% mutate(reason = "irrelevant sitemap - e.g. authors, shop, sport"),
  filtered_html_sitemaps_df  %>% mutate(reason = "entries had HTML contents in sitemap and have been filtered"),
  filtered_global_step_6_excluded_sitemaps_df %>% mutate(reason = "entries had other non related content"),
  missing_sitemap_url        %>% mutate(reason = "entries had missing sitemap_URL and have been removed"),
  missing_sitemap_content    %>% mutate(reason = "entries had missing sitemap_content and have been removed")
) %>%
  transmute(
    type = "sitemap",
    domain = domain_url,
    link = sitemap_URL,
    reason = reason
  ) %>%
  bind_rows(
    
    filtered_dynamic_sitemaps_df %>%
      mutate(reason = "entries were filtered as dynamic websites") %>%
      transmute(
        type = "domain",
        domain = domain_url,
        link = domain_url,
        reason = reason
      )
  )

write.csv(p1_excluded_sitemaps, "/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_excluded_sitemaps.csv", row.names = FALSE)

# Summary 
print(paste(nrow(p1_all_sitemaps), "total entries exported to: p1_all_sitemaps"))
print(paste(nrow(sitemap_scraper_clean_sitemaps), "clean entries exported to: sitemap_scraper_clean_sitemaps"))
print(paste(nrow(p1_excluded_sitemaps), "excluded entries exported to: p1_excluded_sitemaps"))


```


# Step 7:
## This code chunk looks over the whole code and produces a report for every step and prints a deubg file.
### This code runs locally. 
```{r Step 7 }
step_7_generate_final_report <- function() {
  # Create overall summary table
  step_7_overall_summary <- data.frame(
    Step = c(
      "Step 1: Robots.txt URLs Retrieval",
      "Step 2: Robots.txt Contents Retrieval",
      "Step 3: Sitemap URLs Extraction from Robots.txt",
      "Step 4: Typical Sitemap URLs Retrieval",
      "Step 5: Sitemap Contents Retrieval",
      "Step 6: Final Data"
    ),
    Total_Items = c(
      nrow(global_input_all_domains),
      nrow(step_1_domain_urls_robotsUrls_df),
      nrow(step_2_domain_Urls_robotsUrls_robotsContents_df),
      nrow(if (exists("step_4_1_missing_sitemaps_df")) step_4_1_missing_sitemaps_df else data.frame()),
      nrow(if (exists("step_5_valid_sitemaps_check")) step_5_valid_sitemaps_check else data.frame()),
      nrow(step_6_cleaned_df)
    ),
    Successful = c(
      sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt)),
      sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)),
      sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check != "no sitemap"),
      sum(if (exists("step_4_1_missing_sitemaps_df")) !is.na(step_4_1_missing_sitemaps_df$sitemap_URL) else 0),
      sum(if (exists("step_5_valid_sitemaps_check")) !is.na(step_5_valid_sitemaps_check$sitemap_content) else 0),
      sum(!is.na(step_6_cleaned_df$sitemapUrls))
    ),
    Partially_Successful = c(
      sum(is.na(step_1_domain_urls_robotsUrls_df$robots_txt)),
      sum(is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)),
      sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check == "no sitemap"),
      sum(if (exists("step_4_1_missing_sitemaps_df")) is.na(step_4_1_missing_sitemaps_df$sitemap_URL) else 0),
      sum(if (exists("step_5_valid_sitemaps_check")) is.na(step_5_valid_sitemaps_check$sitemap_content) else 0),
      sum(is.na(step_6_cleaned_df$sitemapUrls))
    )
  )

  # Standardize and combine debug DataFrames
  format_debug_df <- function(df, step_name) {
    if (!is.null(df) && nrow(df) > 0) {
      # Define a standard column structure
      standard_columns <- c("Step", "domain_url", "robots_txt", "sitemap_URL", "issue", "note")
      
      # Ensure all required columns exist
      df <- df %>%
        mutate(
          Step = step_name,
          domain_url = if (!"domain_url" %in% colnames(df)) NA else domain_url,
          robots_txt = if (!"robots_txt" %in% colnames(df)) NA else robots_txt,
          sitemap_URL = if (!"sitemap_URL" %in% colnames(df)) NA else sitemap_URL,
          issue = if (!"issue" %in% colnames(df)) NA else issue,
          note = if (!"note" %in% colnames(df)) NA else note
        )
      
      # Reorder columns to match the standard structure
      df <- df[, standard_columns]
      return(df)
    }
    return(NULL)
  }

  # Format all debug DataFrames
  debug_dfs <- list(
    if (exists("step_1_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_1_1_debug_unsuccsesful_fetches_df, "Step 1"),
    if (exists("step_2_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_2_1_debug_unsuccsesful_fetches_df, "Step 2"),
    if (exists("step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df")) format_debug_df(
      step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df %>%
        filter(sitemap_check == "no sitemap") %>%
        mutate(issue = "No sitemap URL"),
      "Step 3"
    ),
    if (exists("step_4_1_missing_sitemaps_df")) format_debug_df(
      step_4_1_missing_sitemaps_df %>%
        filter(is.na(sitemap_URL)) %>%
        mutate(issue = "No typical sitemap URL found"),
      "Step 4"
    ),
    if (exists("step_5_1_debug_unsuccsesful_fetches_df")) format_debug_df(step_5_1_debug_unsuccsesful_fetches_df, "Step 5")
  )

  # Combine all debug DataFrames
  step_7_debug_data <- do.call(rbind, Filter(Negate(is.null), debug_dfs))

  # Save debug data if available
  if (!is.null(step_7_debug_data) && nrow(step_7_debug_data) > 0) {
    write.csv(step_7_debug_data,"/Users/zorbeyozcan/newsmedia_scraper/working_data/sitemap_scraper_output/p1_debug_sitemap_data.csv", row.names = FALSE)
  }


# Generate Markdown report content with "X of Y" formatting
# Generate Markdown report content with "X of Y" formatting
step_7_report_content <- c(
  "# Final Report",
  "## Overall Summary",
  knitr::kable(step_7_overall_summary, format = "markdown"),
  "## Detailed Metrics",
  paste("### Step 1:", paste(sum(!is.na(step_1_domain_urls_robotsUrls_df$robots_txt)), "of", nrow(step_1_domain_urls_robotsUrls_df), "robots.txt URLs retrieved")),
  paste("### Step 2:", paste(sum(!is.na(step_2_domain_Urls_robotsUrls_robotsContents_df$robots_txt_content)), "of", nrow(step_2_domain_Urls_robotsUrls_robotsContents_df), "robots.txt contents retrieved")),
  paste("### Step 3:", paste(sum(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df$sitemap_check != "no sitemap"), "of", nrow(step_3_domain_urls_robotsUrls_robotsContents_sitemapUrlsLocal_df), "sitemap URLs extracted")),
  paste("### Step 4:", paste(sum(!is.na(step_4_1_missing_sitemaps_df$sitemap_URL)), "of", nrow(step_4_1_missing_sitemaps_df), "typical sitemap URLs found")),
  paste("### Step 5:", paste(sum(!is.na(step_5_valid_sitemaps_check$sitemap_content)), "of", nrow(step_5_valid_sitemaps_check), "sitemap contents retrieved")),
  paste("### Step 6: Final dataset includes", paste(nrow(step_6_cleaned_df), "of", nrow(step_6_cleaned_df), "domains")),

  # --- New: Domain summary statistics ---
  "## Domain-Level Summary",
  paste("### Input domains:", length(unique(global_input_all_domains$domain_url))),
  paste("### Domains with valid sitemaps:", length(unique(step_6_cleaned_df$domain_url))),
  paste("### Domains without sitemaps:", 
        length(setdiff(unique(global_input_all_domains$domain_url), unique(step_6_cleaned_df$domain_url))))
)

# Save and render report
step_7_report_path <- "/Users/zorbeyozcan/newsmedia_scraper/documentation/sitema_scraper_report"
writeLines(step_7_report_content, step_7_report_path)
rmarkdown::render(step_7_report_path, output_format = "pdf_document")

print("Final report and debug file created successfully.")
  
}

# Execute the final report generation function
step_7_generate_final_report()

```


# Step 8:
## This code chunk deletes every unnecessary value, function or data.frame in the environment. 
### This code runs locally. 
```{r Step 8 , warning=FALSE}

# Step 5 cleanup
rm(step_5_domain_urls_robotsUrls_robotsContents_sitemapUrls_sitemap_contents, 
   step_5_1_debug_unsuccsesful_fetches_df, step_5_get_sitemap_content_func, 
   step_5_valid_sitemaps_check, step_5_total_valid_sitemaps_check, 
   step_5_loaded_valid_sitemaps_check, domains_with_successful_sitemaps)

# Step 6 cleanup (Keep only the four export data frames)
rm(step_6_cleaned_df, step_6_cleaned_df_fast, step_6_output_path, 
   filtered_media_sitemaps_df, filtered_global_excluded_sitemaps_df, filtered_irrelevant_sitemaps_df,
   filtered_html_sitemaps_df, filtered_global_step_6_excluded_sitemaps_df,
   filtered_dynamic_sitemaps_df, missing_sitemap_url, missing_sitemap_content, 
   failed_sitemaps, all_sitemap_data, export_broken_sitemaps, excluded_domains_df)

# Step 7 cleanup
rm(step_7_overall_summary, step_7_debug_data, step_7_generate_final_report, 
   step_7_report_path, step_7_report_content, debug_dfs, format_debug_df)

# Remove any remaining functions or variables that were not explicitly removed
rm(list = ls(pattern = "^step_"))

print("All functions, values, and data frames have been removed successfully.")

```



