---
title: "urlset_scraper"
author: "Zorbey Özcan"
date: "2025-05-24"
output: html_document
---

# Overview: Sitemap Processing and URLSet Extraction Framework

This document presents a comprehensive R-based framework for the automated retrieval, parsing, filtering, and categorization of sitemaps and associated URLSets from online news domains. The primary goal is to construct a clean, temporally constrained corpus of news article URLs for subsequent analysis. The underlying structure emphasizes modularity, traceability, and replicability, rendering it suitable for academic replication files.

The system leverages a series of interconnected code chunks, each responsible for a distinct operational step. These range from the initialization of logging and data structures to the recursive processing of sitemap layers and the post-processing of scraped content. Throughout, the script implements robust error handling, retry logic, exclusion filtering, date-based heuristics, and output logging to ensure resilience and transparency.

Inputs include a pre-cleaned CSV file listing base sitemap URLs, global date constraints, and filtering criteria. The outputs comprise a set of R data tables that document URLSet contents, processing status, logged errors, and retry metadata. The framework is designed to support iterative refinement, facilitating both full and partial reprocessing cycles in response to blockages or failed requests.


## Code Chunk 1: Initial Setup and Library Loading

### Summary:

This code chunk initializes the R Markdown environment by configuring knitting options and loading all required libraries. It sets global options to suppress messages and warnings during knitting, ensuring cleaner output. Subsequently, it loads a comprehensive set of packages used for data manipulation (`tidyverse`, `data.table`), HTTP requests (`httr`), XML parsing (`xml2`), logging (`futile.logger`), and other utility functions. 

It also programmatically creates two necessary directories: one for storing the output data and another for saving log files. These folders are conditionally created only if they do not already exist. This setup ensures that all subsequent chunks operate within a correctly initialized and reproducible environment.

```{r Step 1: Setup and load required packages}
# knitting Options 
knitr::opts_chunk$set(
  echo    = TRUE,       
  message = FALSE,  
  warning = FALSE    
)

# Load necessary libraries for data manipulation, HTTP requests, XML parsing, and logging
library(tidyverse)
library(httr)
library(xml2)
library(stringr)
library(purrr)
library(gridExtra)
library(grid)
library(data.table)
library(futile.logger)
library(lubridate)

# Create output folder if it does not exist
step_1_output_folder <- "/Users/zorbeyozcan/newsmedia_scraper/working_data/urlset_scraper_output"
if (!dir.exists(step_1_output_folder)) {
  dir.create(step_1_output_folder)
}

# Create logging folder if it does not exist
step_1_logging_folder <- "/Users/zorbeyozcan/newsmedia_scraper/documentation"
if (!dir.exists(step_1_logging_folder)) {
  dir.create(step_1_logging_folder)
}


cat("Step 1 completed: Packages loaded and output folder created.\n")

```

## Code Chunk 2: Load Input CSV File

### Summary:

This code chunk loads the core input data required for the entire scraping workflow. Specifically, it reads a pre-cleaned CSV file containing base sitemap URLs using the `fread()` function from the `data.table` package. This method is optimized for fast reading of large tabular data, ensuring efficient initialization of the dataset.

The resulting object, `step_2_input_dt`, serves as the foundational input table for subsequent sitemap processing steps. It contains information such as domain identifiers and first-level sitemap URLs. No transformations or filters are applied at this stage; the goal is to load the raw input as-is into memory.

```{r Step 2: Load Input CSV File}
# Load the input CSV file into a data.table using fread
step_2_input_dt <- fread("/Users/zorbeyozcan/newsmedia_scraper/data/sitemap_scraper_clean_sitemaps.csv", stringsAsFactors = FALSE)


cat("Step 2 completed: Input CSV file loaded.\n")

```

## Code Chunk 3: Set Global Parameters, Exclusions, and User Agents

### Summary:

This code chunk defines a set of global parameters that govern filtering and request behavior throughout the scraping process. First, it specifies the temporal boundaries (`global_date_start`, `global_date_end`) within which sitemaps and URLs are considered relevant. Second, it creates a vector of exclusion keywords (`global_excluded_strings`), which are used to eliminate URLs containing unwanted thematic elements such as images, videos, or sports content.

In addition, the chunk retrieves the current VPN IP address for logging purposes. It also defines five user-agent profiles simulating different browser environments across operating systems, which are subsequently combined into a rotation list (`global_user_agent_list`). This rotation mechanism supports anonymity and helps mitigate the risk of request blocking during repeated access to remote servers.

```{r Step 3: Set Global Parameters, Exclusions, and User Agents}
# Set global variables for the date range
global_date_start <- as.Date("2025-01-01")
global_date_end   <- as.Date("2025-02-23")

# Set global variables for wayback validation later on
global_wayback_date_start <- as.Date("2025-01-01")
global_wayback_date_end   <- as.Date("2025-03-31")

# Set global list of excluded strings (URLs containing these strings will be excluded)
global_excluded_strings <- c(
  "image", "bilder", "picture", "fotografie", "photo", "foto", "imagegallery", "gallery",
  "video", "media", "audio", "podcasts", "podcast",       
  "themen.*-az", "topics", "topic", "author", "sport", "shop", "security"    
)

# Retrieve the current VPN IP address and trim any whitespace
global_vpn_ip <- trimws(suppressWarnings(readLines("https://ifconfig.me/ip")))

# Define global user agent profiles
global_user_agent_profile_1 <- "Mozilla/5.0 (Macintosh; Intel Mac OS X 13_3_1) AppleWebKit/605.1.15 (KHTML, like Gecko) Version/17.4 Safari/605.1.15"
global_user_agent_profile_2 <- "Mozilla/5.0 (Macintosh; Intel Mac OS X 12_6_8) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/120.0.6099.129 Safari/537.36"
global_user_agent_profile_3 <- "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/122.0.6261.94 Safari/537.36"
global_user_agent_profile_4 <- "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/117.0.5938.92 Safari/537.36"
global_user_agent_profile_5 <- "Mozilla/5.0 (Windows NT 10.0; Win64; x64; rv:109.0) Gecko/20100101 Firefox/117.0"

# Create global user agent rotation list
global_user_agent_list <- c(
  global_user_agent_profile_1,
  global_user_agent_profile_2,
  global_user_agent_profile_3,
  global_user_agent_profile_4,
  global_user_agent_profile_5
)


cat("Step 3 completed: Global parameters, excluded lists, VPN IP, and user agents initialized.\n")

```

## Code Chunk 4: Create Global Data Tables for Error Logging, Retry Handling, and Master Rotation Tracking

### Summary:

This code chunk initializes two key global data structures required for tracking the scraping process and its failures. The first structure, `global_error_dt`, is a logging table that records all non-response-based errors occurring during sitemap processing. Each entry includes metadata such as domain and URL identifiers, error category, processing flags, and timestamps, enabling detailed post-hoc diagnostics and auditability.

The second structure, `global_master_dt`, serves as a master registry for tracking the state and progress of each top-level sitemap URL. It records high-level indicators such as the number of requests made, scraping success, user agent ID, and the overall processing status. These tables do not take external inputs but are dynamically populated and updated throughout the execution of subsequent chunks. They serve as essential control and documentation mechanisms across the entire pipeline.

```{r Step 4: Create Global Data Tables for Error Logging, Retry Handling, and Master Rotation Tracking}
# Create the global error data table for non-response-based sitemap processing errors
global_error_dt <- data.table(
  domain_id              = integer(),      # Unique ID for the domain
  domain_url             = character(),    # Domain URL
  layer_1_url_id         = integer(),      # Unique ID for the top-level sitemap
  layer_1_url            = character(),    # Top-level sitemap URL
  error_url_id           = integer(),      # ID of the problematic sub-URL (from progression)
  error_url              = character(),    # Sub-sitemap or link that caused the error
  parent_url_id          = integer(),      # ID of the parent sitemap URL
  root_tag               = character(),    # Root tag if known ("urlset", "sitemapindex", "unknown", etc.)
  error_category         = character(),    # Class of error (e.g. "xml_parse_error", "excluded_string", "missing_root_tag", ...)
  processed_flag         = logical(),      # Was this URL marked as processed in progression_dt?
  retry_flag             = logical(),      # Should the entry be retried? 
  timestamp              = as.POSIXct(character()),  # Timestamp of logging
  source_function        = character(),    # Where the error was triggered (e.g. "step_6", "step_8", "step_9")
  status_code            = integer()       # HTTP status if applicable
)

# Create the global master data table for tracking the overall status of each sitemap/domain
global_master_dt <- data.table(
  domain_id              = integer(),      # Unique ID for the domain
  domain_url             = character(),    # Domain URL
  layer_1_url_id         = integer(),      # Unique ID for the sitemap
  layer_1_url            = character(),    # Sitemap URL
  input_processing_status= character(),    # Current status (e.g., "ok", "suspicious", "moved to retry")
  total_request_count    = integer(),      # Tracks requests for an input sitemap
  total_urlsets_scraped  = integer(),      # Tracks total urlsets scraped
  last_checked           = as.POSIXct(character()),  # Timestamp of the last check
  current_user_agent_id  = integer(),      # ID of the currently used User-Agent profile
  processing_flag        = character()     # Indicates processing status of the input
)


cat("Step 4 completed: Global error and master data tables created.\n")

```

## Code Chunk 5: Defining Date-Check Helper Functions

### Summary:

This chunk introduces two central helper functions for date-based filtering, which is a core mechanism for selecting relevant sitemap entries. Both functions serve to determine whether either sitemap XML metadata or URL structures contain date information that falls within a predefined global range (`global_date_start` to `global_date_end`). These checks ensure that only temporally relevant content is included in downstream processing.

The functions do not generate persistent outputs but return structured lists that guide decisions on exclusion or continuation. They are used extensively in the filtering, sorting, and scraping routines that follow, and are thus foundational to the system’s temporal logic.

#### Function: `step_5_1_date_check_urlset_func`

This function processes an XML document of type `<urlset>` and extracts all `<lastmod>` elements using a provided namespace map. It then converts these timestamp strings into R `Date` objects, filters invalid entries, and checks whether any date falls within the defined global range. If matching dates are found, it returns `"proceed"` with a reason `"in_range"` and the earliest valid date. Otherwise, it returns `"exclude"` or `"proceed"` with appropriate reasons based on the presence or absence of valid tags. This function operates directly on parsed XML structures and supports namespace-aware extraction.

#### Function: `step_5_2_date_check_link_func`

This function applies regular expressions to detect embedded date patterns within URL strings. It supports a wide range of date formats (e.g., `YYYY-MM-DD`, `DDMMYYYY`, `monthnameYYYY`), both compact and delimited, using localized and international month names. Upon detecting a valid pattern, it computes a derived date and checks whether it overlaps with the global date interval. It then returns a decision, a reason, and the matched pattern, along with computed start and end dates. The function is designed to handle noisy or underspecified URLs and is robust against malformed or ambiguous input.

```{r Step 5: Defining date-check helper functions:}
# Function: step_5_1_date_check_urlset_func
# This function extracts <lastmod> tags from a URLset XML document,
# converts them to dates, and checks if any date falls within the specified date range.
# It returns a list with a decision ("proceed" or "exclude"), a reason, and a representative detected date.
step_5_1_date_check_urlset_func <- function(xml_doc, ns_map, date_from, date_to) {
  # Extract the text of all <lastmod> tags using the provided namespace map
  step_5_1_lastmods <- xml_find_all(xml_doc, ".//ns:lastmod", ns = ns_map) %>% xml_text()
  # Remove any time portion and convert to Date objects
  step_5_1_lastmod_dates <- as.Date(gsub("T.*", "", step_5_1_lastmods), format = "%Y-%m-%d")
  # Remove NA dates
  step_5_1_lastmod_dates <- step_5_1_lastmod_dates[!is.na(step_5_1_lastmod_dates)]
  
  if (length(step_5_1_lastmod_dates) == 0) {
    return(list(decision = "proceed", reason = "no_lastmod_found", detected_date = NA))
  }
  
  if (any(step_5_1_lastmod_dates >= date_from & step_5_1_lastmod_dates <= date_to)) {
    # Use the minimum date that falls within the range as a representative detected date
    step_5_1_detected_date <- min(step_5_1_lastmod_dates[step_5_1_lastmod_dates >= date_from & step_5_1_lastmod_dates <= date_to])
    return(list(decision = "proceed", reason = "in_range", detected_date = step_5_1_detected_date))
  } else {
    return(list(decision = "exclude", reason = "out_of_range", detected_date = NA))
  }
}

# Function: step_5_2_date_check_link_func
# This function checks a URL string for date patterns using regular expressions.
# It determines whether the detected date (if any) falls within the specified date range.
# It returns a list with a decision, a reason, and the detected date.
step_5_2_date_check_link_func <- function(url, date_from, date_to) {

  step_5_2_url_clean <- tolower(url)

  if (is.null(url) || length(url) != 1 || is.na(url) || !nzchar(url)) {
    return(list(decision = "proceed", reason = "no_date", detected_date = NA, matched_pattern = "none"))
  }

  # valid seperators 
  sep <- "[-_\\/]"
  
  # Year only 
  step_5_2_year_pattern <- "(?<!\\d)((?:19|20)\\d{2})(?!\\d)"
  
  # YYYY<sep>MM<sep>DD
  step_5_2_year_month_day_pattern <- paste0(
    "(?<!\\d)",
    "((?:19|20)\\d{2})", sep,
    "(0[1-9]|1[0-2])",      sep,
    "(0[1-9]|[12][0-9]|3[01])",
    "(?!\\d)"
  )
  
  # YYYYMMDD compact
  step_5_2_compact_year_month_day_pattern <- "(?<!\\d)((?:19|20)\\d{2})(0[1-9]|1[0-2])(0[1-9]|[12][0-9]|3[01])(?!\\d)"
  
  # YYYY<sep>MM
  step_5_2_year_month_pattern <- paste0(
    "(?<!\\d)",
    "((?:19|20)\\d{2})", sep,
    "(0[1-9]|1[0-2])",
    "(?!\\d)"
  )
  
  # YYYYMM compact
  step_5_2_compact_year_month_pattern <- "(?<!\\d)((?:19|20)\\d{2})(0[1-9]|1[0-2])(?!\\d)"
  
  # MM<sep>YYYY
  step_5_2_month_year_pattern <- paste0(
    "(?<!\\d)",
    "([1-9]|0[1-9]|1[0-2])", sep,
    "((?:19|20)\\d{2})",
    "(?!\\d)"
  )
  
  # DD<sep>MM<sep>YYYY
  step_5_2_day_month_year_pattern <- paste0(
    "(?<!\\d)",
    "(0[1-9]|[12][0-9]|3[01])", sep,
    "(0[1-9]|1[0-2])",           sep,
    "((?:19|20)\\d{2})",
    "(?!\\d)"
  )
  
  # DDMMYYYY compact
  step_5_2_compact_day_month_year_pattern <- "(?<!\\d)([0-3][0-9])([0][1-9]|[12][0-9]|3[01])((?:19|20)\\d{2})(?!\\d)"

  step_5_2_short_months <- c("jan", "feb", "mär", "mae", "mar", "apr", "mai", "may", "jun", "jul", "aug", "sep", "okt", "oct", "nov", "dez", "dec")
  step_5_2_long_months <- c("january", "february", "march", "april", "may", "june", "july", "august", "september", "october", "november", "december",
                            "januar", "februar", "märz", "maerz", "april", "mai", "juni", "juli", "august", "september", "oktober", "november", "dezember")
  step_5_2_all_months_pattern <- paste0("(", paste(c(step_5_2_short_months, step_5_2_long_months), collapse = "|"), ")")

  step_5_2_monthname_year_pattern <- paste0(step_5_2_all_months_pattern, "(20\\d{2}|19\\d{2})")
  step_5_2_year_monthname_pattern <- paste0("(20\\d{2}|19\\d{2})", step_5_2_all_months_pattern)

  start_date <- end_date <- detected_date <- NA
  matched_pattern <- NULL

  # Collect all possible matches with positions
  patterns <- list(
    ymd_sep = step_5_2_year_month_day_pattern,
    ymd_compact = step_5_2_compact_year_month_day_pattern,
    dmy_sep = step_5_2_day_month_year_pattern,
    dmy_compact = step_5_2_compact_day_month_year_pattern,
    month_year = step_5_2_month_year_pattern,
    year_month = step_5_2_year_month_pattern,
    ym_compact = step_5_2_compact_year_month_pattern,
    monthname_year = step_5_2_monthname_year_pattern,
    year_monthname = step_5_2_year_monthname_pattern,
    year_only = step_5_2_year_pattern
  )

  matches <- do.call(rbind, lapply(names(patterns), function(name) {
    loc <- str_locate_all(step_5_2_url_clean, patterns[[name]])[[1]]
    if (nrow(loc) > 0) {
      data.frame(pattern = name, start = loc[,1], stringsAsFactors = FALSE)
    }
  }))
  
  if (is.null(matches) || nrow(matches) == 0) {
    return(list(
      decision        = "proceed",
      reason          = "no_date",
      detected_date   = as.Date(NA),
      matched_pattern = NA_character_
    ))
  }
  # Choose the first occurrence
  first_match <- matches[which.min(matches$start), ]
  pattern <- first_match$pattern

  # Process based on chosen pattern
  if (pattern == "ymd_sep") {
    parts <- str_match(step_5_2_url_clean, step_5_2_year_month_day_pattern)
    year  <- as.integer(parts[1,2]); month <- as.integer(parts[1,3]); day   <- as.integer(parts[1,4])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "ymd"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "ymd_compact") {
    parts <- str_match(step_5_2_url_clean, step_5_2_compact_year_month_day_pattern)
    year  <- as.integer(parts[1,2]); month <- as.integer(parts[1,3]); day   <- as.integer(parts[1,4])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "ymd_compact"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "dmy_sep") {
    parts <- str_match(step_5_2_url_clean, step_5_2_day_month_year_pattern)
    day   <- as.integer(parts[1,2]); month <- as.integer(parts[1,3]); year  <- as.integer(parts[1,4])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "dmy"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "dmy_compact") {
    parts <- str_match(step_5_2_url_clean, step_5_2_compact_day_month_year_pattern)
    day   <- as.integer(parts[1,2]); month <- as.integer(parts[1,3]); year  <- as.integer(parts[1,4])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "dmy_compact"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "month_year") {
    parts <- str_match(step_5_2_url_clean, step_5_2_month_year_pattern)
    month <- as.integer(parts[1,2]); year  <- as.integer(parts[1,3])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "month_year"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "year_month") {
    parts <- str_match(step_5_2_url_clean, step_5_2_year_month_pattern)
    year  <- as.integer(parts[1,2]); month <- as.integer(parts[1,3])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "ym"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "ym_compact") {
    parts <- str_match(step_5_2_url_clean, step_5_2_compact_year_month_pattern)
    year  <- as.integer(parts[1,2]); month <- as.integer(parts[1,3])
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month)); pattern <- "ym_compact"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "monthname_year") {
    parts <- str_match(step_5_2_url_clean, step_5_2_monthname_year_pattern)
    month_name <- tolower(parts[1,2]); year <- as.integer(parts[1,3])
    month_number <- match(month_name, tolower(c(step_5_2_short_months, step_5_2_long_months)))
    if (month_number > length(step_5_2_short_months)) month_number <- month_number - length(step_5_2_short_months)
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month_number)); pattern <- "monthname_year"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "year_monthname") {
    parts <- str_match(step_5_2_url_clean, step_5_2_year_monthname_pattern)
    year <- as.integer(parts[1,2]); month_name <- tolower(parts[1,3])
    month_number <- match(month_name, tolower(c(step_5_2_short_months, step_5_2_long_months)))
    if (month_number > length(step_5_2_short_months)) month_number <- month_number - length(step_5_2_short_months)
    detected_date <- as.Date(sprintf("%04d-%02d-01", year, month_number)); pattern <- "ym_monthname"
    start_date <- detected_date; end_date <- start_date + months(1) - days(1)

  } else if (pattern == "year_only") {
    parts <- str_match(step_5_2_url_clean, step_5_2_year_pattern)
    year <- as.integer(parts[1,2])
    detected_date <- as.Date(sprintf("%04d-01-01", year)); pattern <- "year_only"
    start_date <- detected_date; end_date <- as.Date(sprintf("%04d-12-31", year))
  }

  # Global range check
  if (start_date <= date_to && end_date >= date_from) {
    return(list(decision = ifelse(pattern == "year_only" && is.na(detected_date), "proceed", "proceed"),
                reason   = ifelse(pattern == "year_only", ifelse(start_date <= date_to && end_date >= date_from, "in_range", "out_of_range"), "in_range"),
                detected_date = detected_date,
                matched_pattern = pattern,
                start_date = start_date,
                end_date = end_date))
  } else {
    return(list(decision = "exclude",
                reason = "out_of_range",
                detected_date = detected_date,
                matched_pattern = pattern,
                start_date = start_date,
                end_date = end_date))
  }
}

cat("Step 5 completed: Date check functions defined.\n")

```

## Code Chunk 6: Defining Sorting Functions

### Summary:

This code chunk introduces core sorting logic for sitemap sub-entries. The goal is to exclude irrelevant links, assign a meaningful order to those retained, and facilitate the processing of entries that lack temporal metadata. The process combines regular expression-based filtering with a pagination grouping heuristic. Two functions are defined: one for assigning pagination groups, and one for orchestrating the overall filtering and ordering.

The function `step_6_sorting_func` takes as input a vector of URLs and multiple metadata parameters (e.g., identifiers, domain info, global exclusion criteria). Its output is a `data.table` annotated with filtering decisions, group membership, and sort indices, which is used to update the global progression tracking structure.

### Function: `step_6_1_grouping_func`

This helper function processes links that lack explicit date information and attempts to infer pagination groupings based on filename patterns. It extracts numeric suffixes from filenames and groups entries with shared prefixes. Only groups with five or more entries are retained. Group identifiers (`pagination_group`) and within-group order (`pagination_index`) are assigned accordingly. For each group member, the progression tracking table is updated via `step_7_1_progression_update`.

### Function: `step_6_sorting_func`

This is the main sorting routine. It applies exclusion filters based on known undesired substrings (`global_excluded_strings`) and date range evaluation using `step_5_2_date_check_link_func`. Remaining links are either kept, grouped by pagination logic, or sorted in default order. It handles multiple edge cases (e.g., links with no dates or partial information) and ensures each retained link receives a `sort_place` value. Additionally, it updates a global environment progression object, enabling traceability and stateful tracking across nested sitemap structures. The function returns a complete `data.table` capturing the filtering, grouping, and sorting status of each processed link.


```{r Step 6: Defining sorting functions:}
# Function: step_6_1_grouping_func
# This function takes a data.table of links marked as 'no_date' and attempts to group them into pagination groups based on similar basename patterns.
# If a group has fewer than 10 entries or missing numeric indicators, it is flagged as 'individual'; else a pagination_group and pagination_index are assigned.

step_6_1_grouping_func <- function(step_6_1_links_dt,
                                   domain_id,
                                   domain_url,
                                   layer_1_url_id,
                                   layer_1_url,
                                   parent_url_id) {

  # Extract key and number
  step_6_1_links_dt[, group_key := str_replace(basename(link), "-\\d+(?=\\.xml$)", "")]
  step_6_1_links_dt[, group_num := as.integer(str_extract(basename(link), "\\d+(?=\\.xml$)"))]

  # Init columns
  step_6_1_links_dt[, `:=`(
    pagination_group = NA_character_,
    pagination_index = NA_integer_
  )]

  # Identify valid groups
  group_counts <- step_6_1_links_dt[!is.na(group_num), .N, by = group_key]
  valid_groups <- group_counts[N >= 5, group_key]

  for (g in valid_groups) {
    idx <- which(step_6_1_links_dt$group_key == g)
    ordered_idx <- idx[order(step_6_1_links_dt$group_num[idx])]

    group_links <- step_6_1_links_dt$link[ordered_idx]

    # Update progression for each group member
    for (i in seq_along(group_links)) {
      step_7_1_progression_update(
        domain_id         = domain_id,
        domain_url        = domain_url,
        layer_1_url_id    = layer_1_url_id,
        layer_1_url       = layer_1_url,
        current_url       = group_links[i],
        parent_url_id     = parent_url_id,
        pagination_group  = g,
        pagination_index  = i,
        pagination_group_status = "candidate"
      )
    }
  }
  return(step_6_1_links_dt)
}

step_6_sorting_func <- function(step_6_links_vector, 
                                layer_1_url_id, 
                                layer_1_url,          
                                parent_url, 
                                parent_url_id,
                                global_date_start, 
                                global_date_end, 
                                global_excluded_strings,
                                domain_id = NA_integer_,
                                domain_url = NA_character_) {
  
  prog_name <- paste0("sitemap_id_", layer_1_url_id, "_progression_dt")

  # Initialize internal data.table
  step_6_sort_list_dt <- data.table::data.table(
    link = step_6_links_vector,
    in_range = NA_character_,
    excluded = NA_character_,
    sort_place = NA_integer_,
    pagination_group = NA_character_,
    pagination_index = NA_integer_
  )
  
  # Exclude links containing excluded strings
  excluded_pattern <- paste(global_excluded_strings, collapse = "|")
  step_6_sort_list_dt[stringr::str_detect(link, excluded_pattern), excluded := "by_string"]
  
  # Apply date check on remaining links
  for (i in which(is.na(step_6_sort_list_dt$excluded))) {
    check_result <- step_5_2_date_check_link_func(step_6_sort_list_dt$link[i], global_date_start, global_date_end)
    
    if (check_result$reason == "out_of_range") {
      step_6_sort_list_dt[i, excluded := "by_date"]
    } else if (check_result$reason == "in_range") {
      step_6_sort_list_dt[i, `:=`(in_range = "yes", excluded = "no")]
    } else {
      step_6_sort_list_dt[i, `:=`(in_range = "unknown", excluded = "no")]
    }
  }
  
  # Group only the “no-date” links into pagination groups of size ≥10
  subset_idx <- which(
  step_6_sort_list_dt$excluded == "no" &
  step_6_sort_list_dt$in_range == "unknown"
  )
  
  subset_dt  <- step_6_sort_list_dt[subset_idx]
  grouped_dt <- step_6_1_grouping_func(
    step_6_1_links_dt = subset_dt,
    domain_id         = domain_id,
    domain_url        = domain_url,
    layer_1_url_id    = layer_1_url_id,
    layer_1_url       = layer_1_url,
    parent_url_id     = parent_url_id
  )
  
  step_6_sort_list_dt[subset_idx, pagination_group := grouped_dt$pagination_group]
  step_6_sort_list_dt[subset_idx, pagination_index := grouped_dt$pagination_index]
  
  # Assign sort_places for in-range links
  step_6_sort_list_dt[in_range == "yes", 
    sort_place := seq_len(.N)
  ]

  next_base <- function(dt) {
    mx <- suppressWarnings(max(dt$sort_place, na.rm = TRUE))
    if (!is.finite(mx)) 0L else mx
  }
  
  # grouped no-date links (in_range == "unknown")
   remaining_dt <- step_6_sort_list_dt[
    excluded == "no" & in_range == "unknown" &
    is.na(pagination_group)
  ]
  if (nrow(remaining_dt) > 0) {
    start <- next_base(step_6_sort_list_dt)
    step_6_sort_list_dt[link %in% remaining_dt$link,
      sort_place := start + seq_len(nrow(remaining_dt))
    ]
  }
  
  # ungrouped no-date links
  grouped_dt <- step_6_sort_list_dt[
    excluded == "no" & in_range == "unknown" &
    !is.na(pagination_group)
  ][order(pagination_group, pagination_index)]
  if (nrow(grouped_dt) > 0) {
    start <- next_base(step_6_sort_list_dt)
    step_6_sort_list_dt[link %in% grouped_dt$link,
      sort_place := start + seq_len(nrow(grouped_dt))
    ]
  }
  
  # Mark excluded links as processed
  step_6_sort_list_dt[excluded == "by_string", `:=`(
    processed = TRUE,
    processing_status = "excluded_by_string",
    sorted = "excluded"
  )]
  step_6_sort_list_dt[excluded == "by_date", `:=`(
    processed = TRUE,
    processing_status = "excluded_by_date",
    sorted = "excluded"
  )]
  
  # Mark remaining as unprocessed 
  step_6_sort_list_dt[is.na(processed), processed := FALSE]
  step_6_sort_list_dt[is.na(processing_status), processing_status := "in_progress"]
  step_6_sort_list_dt[is.na(sorted), sorted := "yes"]
  
  # updateing sorted sitemap
  parent_row_id <- get(prog_name, envir = .GlobalEnv)[current_url == parent_url, current_url_id]

  step_7_1_progression_update(
    domain_id      = domain_id,
    domain_url     = domain_url,
    layer_1_url_id = layer_1_url_id,
    layer_1_url    = layer_1_url,   
    current_url    = parent_url,    
    parent_url_id  = parent_url_id, 
    processing_status = "subsitemap_sorted",
    root_tag          = "sitemapindex",
    subsitemap_status = "in_progress",
    subsitemap_progress = paste0("0 of ", nrow(step_6_sort_list_dt)),
    sort_order       = list(step_6_sort_list_dt)
  )
  
  # child link entries
  for (i in seq_len(nrow(step_6_sort_list_dt))) {
    row <- step_6_sort_list_dt[i]
  
    step_7_1_progression_update(
      domain_id        = domain_id,
      domain_url       = domain_url,
      layer_1_url_id   = layer_1_url_id,
      layer_1_url      = layer_1_url,
      current_url      = row$link,
      parent_url_id    = parent_row_id,        
      in_range         = row$in_range,
      root_tag         = "unknown",
      sort_place       = row$sort_place,
      pagination_group = row$pagination_group,
      pagination_index = row$pagination_index,
      processed        = row$processed,
      processing_status= row$processing_status,
      sorted           = row$sorted
    )
  }
  
  return(step_6_sort_list_dt)
}


cat("Step 6 completed: Sorting function defined.\n")

```

## Code Chunk 7: Defining Core Functions for Processing Sitemaps

### Summary:

This section defines the central orchestration functions responsible for managing the lifecycle of sitemap processing within the global scraping framework. The logic ensures consistent tracking, logging, classification, and storage of sitemap states. This includes dynamically updating metadata tables (`progression_dt`, `master_dt`, `response_log_dt`) and parsing valid XML structures for URL data extraction. The functions operate in a state-aware and fault-tolerant manner, integrating seamlessly into prior structures defined in previous chunks.

Four functions are defined: a progression table updater, a master control updater, an HTTP response logger, and the actual URLSET parser. Together, they implement a robust control-flow regime capable of supporting complex sitemap hierarchies and pagination patterns under unreliable network conditions.

#### Function: `step_7_1_progression_update`

This function maintains and updates a per-sitemap `progression_dt`, which tracks all sub-URLs and their processing status. It inserts new rows or modifies existing entries, incorporating metadata such as sort position, pagination grouping, processing status, and timestamp. Additionally, it handles group-level logic for pagination heuristics—aborting further requests if multiple consecutive entries lie outside the desired date range. It also dissolves invalidated groups if higher-level sitemap structures (e.g. `sitemapindex`) are detected among them.

#### Function: `step_7_2_master_dt_update_func`

This function updates the global-level `master_dt`, reflecting the overall status of each `layer_1_url`. It incorporates information from `progression_dt`, `response_log_dt`, and `output_dt` to assess whether a sitemap is fully processed, partially failed, or still in progress. It also determines whether retry logic should be applied based on log history and request flags. Metrics such as total request count and user agent usage are maintained for auditability.

#### Function: `step_7_3_response_log_update_func`

This function creates and updates a `response_log_dt` for each sitemap, logging all non-200 HTTP responses. It classifies the error into categories (e.g. soft block, hard block), tracks the frequency of error types, and decides whether to escalate the situation (e.g. initiating retry behavior). Response metadata such as status codes, headers, and body snippets are recorded for post-hoc inspection. Additionally, the associated entry in the `progression_dt` is updated accordingly.

#### Function: `step_7_4_urlset_scraper_func`

This function parses XML responses of type `<urlset>`, extracts relevant `<loc>` and `<lastmod>` entries, and determines if the URLs fall within a pre-defined date range. If valid, the content is stored in a dedicated `output_dt`. The function includes logic for compressed XML files (`.gz`) and handles malformed XML via structured error logging. It also integrates pagination-aware logic, allowing the dynamic classification of groups as "before range" and aborting redundant requests. The function returns a summary of detected links, validity, and temporal span.

```{r Step 7: Defining core functions for processing sitemaps:}
# The function step_7_1_progression_update  updates the progression data table for a sitemap.
# It inserts new entries or updates existing ones, applies defaults,
# updates subsitemap_progress, and marks fully processed parents.

step_7_1_progression_update <- function(
  domain_id,
  domain_url,
  layer_1_url_id,
  layer_1_url,
  current_url,
  parent_url_id = NA_integer_,
  root_tag = "unknown",
  processed = FALSE,
  processing_status = "in_progress",
  sorted = "no",
  sort_place = NA_integer_,
  in_range = "unknown",
  subsitemap_status = "in_progress",
  sort_order = list(data.table()),
  subsitemap_progress = "in_progress",
  pagination_group = NA_character_,
  pagination_index = NA_integer_,
  pagination_group_status = NA_character_
) {
  rt <- root_tag
  step_7_progression_dt_name <- paste0("sitemap_id_", layer_1_url_id, "_progression_dt")

  # create new if not existing 
  if (!exists(step_7_progression_dt_name, envir = .GlobalEnv)) {
    assign(step_7_progression_dt_name, data.table(
      domain_id                    = integer(),
      domain_url                   = character(),
      layer_1_url_id               = integer(),
      layer_1_url                  = character(),
      current_url_id               = integer(),
      current_url                  = character(),
      parent_url_id                = integer(),
      processed                    = logical(),
      processing_status            = character(),
      sorted                       = character(),
      sort_place                   = integer(),
      in_range                     = character(),
      root_tag                     = character(),
      subsitemap_status            = character(),
      sort_order                   = list(data.table()),
      subsitemap_progress          = character(),
      pagination_group             = character(),
      pagination_index             = integer(),
      pagination_group_status      = character(),
      timestamp                    = as.POSIXct(character())
    ), envir = .GlobalEnv)
  }

  step_7_progression_dt <- get(step_7_progression_dt_name, envir = .GlobalEnv)
  if (!"pagination_group_status" %in% colnames(step_7_progression_dt)) {
    step_7_progression_dt[, pagination_group_status := NA_character_]
  }
  existing_idx <- which(step_7_progression_dt$current_url == current_url)

  # update existing with root tag "urlset" or "unknown" 
  if (length(existing_idx) > 0) {
    new_rt <- rt
    step_7_progression_dt[existing_idx, `:=`(
      domain_id          = domain_id,
      domain_url         = domain_url,
      layer_1_url_id     = layer_1_url_id,
      layer_1_url        = layer_1_url,
      parent_url_id      = parent_url_id,
      processed          = ..processed,
      processing_status  = ..processing_status,
      sorted             = sorted,
      sort_place         = sort_place,
      in_range           = ..in_range,
      root_tag           = ifelse(step_7_progression_dt$root_tag[existing_idx] == "unknown",
                                  new_rt,
                                  step_7_progression_dt$root_tag[existing_idx]),
      
      subsitemap_status            = ifelse(rt %in% c("urlset","unknown"),
                                             "not_a_sitemap",
                                             subsitemap_status),
      
      sort_order                   = list(data.table()),
      
      subsitemap_progress          = ifelse(rt %in% c("urlset","unknown"),
                                             "not_a_sitemap",
                                             subsitemap_progress),
      
      pagination_group             = ifelse(!is.na(..pagination_group),
                                   ..pagination_group,
                                   pagination_group),
      
      pagination_index             = ifelse(!is.na(..pagination_index),
                                   ..pagination_index,
                                   pagination_index),
      
      pagination_group_status     = ifelse(!is.na(..pagination_group_status),
                                   ..pagination_group_status,
                                   pagination_group_status),
      
      timestamp                    = Sys.time()
    )]
    
    
  }
  
  if (!is.null(pagination_group_status) && length(existing_idx) > 0) {
  step_7_progression_dt[existing_idx, pagination_group_status := pagination_group_status]
}
  
  else {
    
    # add new row 
    new_id <- if (nrow(step_7_progression_dt) == 0) 1 else max(step_7_progression_dt$current_url_id, na.rm = TRUE) + 1
    step_7_new_row <- data.table(
      domain_id                    = domain_id,
      domain_url                   = domain_url,
      layer_1_url_id               = layer_1_url_id,
      layer_1_url                  = layer_1_url,
      current_url_id               = new_id,
      current_url                  = current_url,
      parent_url_id                = parent_url_id,
      processed                    = processed,
      processing_status            = processing_status,
      sorted                       = sorted,
      sort_place                   = sort_place,
      in_range                     = in_range,
      root_tag                     = rt,
      subsitemap_status            = ifelse(rt %in% c("urlset","unknown"),
                                             "not_a_sitemap",
                                             subsitemap_status),
      sort_order                   = list(data.table()),
      subsitemap_progress          = ifelse(rt %in% c("urlset","unknown"),
                                             "not_a_sitemap",
                                             subsitemap_progress),
      pagination_group             = pagination_group,
      pagination_index             = pagination_index,
      pagination_group_status      = pagination_group_status,
      timestamp                    = Sys.time()
    )
    step_7_progression_dt <- rbind(step_7_progression_dt, step_7_new_row, fill = TRUE)
  }

  ## Override if roottag "sitemapindex"
  parent_indices <- which(step_7_progression_dt$root_tag == "sitemapindex")
  status_ok  <- c("excluded_by_string","excluded_by_date","scraped","all_child_links_processed")
  status_err <- c("response_error","xml_error","unsupported_root_tag","all_processed_some_errors")

  for (p_idx in parent_indices) {
    kids  <- step_7_progression_dt[parent_url_id == step_7_progression_dt$current_url_id[p_idx]]
    stats <- kids$processing_status
    n_kids <- length(stats)
    processed_count <- sum(stats %in% c(status_ok, status_err))

      
    if (n_kids > 0 && all(stats %in% status_ok)) {
      # all childs processed & no error 
      step_7_progression_dt[p_idx, `:=`(
        processed         = TRUE,
        processing_status = "all_child_links_processed",
        subsitemap_status = "fully_processed",
        subsitemap_progress = paste0(n_kids, " of ", n_kids)
      )]
    } else if (n_kids > 0 && all(stats %in% c(status_ok, status_err))) {
      # all childs processed & at least one error 
      step_7_progression_dt[p_idx, `:=`(
        processed         = FALSE,
        processing_status = "all_processed_some_errors",
        subsitemap_status = "partially_failed",
        subsitemap_progress = paste0(processed_count, " of ", n_kids)
      )]
    } else {
      # at one child is in_progress 
      step_7_progression_dt[p_idx, `:=`(
        processed         = FALSE,
        processing_status = "in_progress",
        subsitemap_status = "in_progress",
        subsitemap_progress = paste0(processed_count, " of ", n_kids)
      )]
    }
  }

  ## Override if roottag "urlset" + in valid group
  .grp_id <- pagination_group
  err_vec <- c("response_error", "xml_error", "unsupported_root_tag")
  if (rt == "urlset" && !is.na(pagination_group)) {
  
    # pull all rows of this group
    grp_rows <- step_7_progression_dt[pagination_group == .grp_id][order(pagination_index)]
    if (!is.na(pagination_group_status) && pagination_group_status == "valid_up") {
    grp_rows <- grp_rows[order(-pagination_index)]
    
    } else {
      grp_rows <- grp_rows[order(pagination_index)]
    }
  
    # check if three in a row lay before the date range 
    status_vec <- grp_rows$pagination_group_status
    runs       <- rle(status_vec)                       # Run-Length-Encoding
    abort_now  <- any(runs$values == "date_before_range" & runs$lengths >= 3)
    
    if (abort_now) {
      abort_idx <- which(step_7_progression_dt$pagination_group == pagination_group &
                         !step_7_progression_dt$processed &
                         !step_7_progression_dt$processing_status %in% err_vec)
    
      if (length(abort_idx) > 0) {
        step_7_progression_dt[abort_idx, `:=`(
          processed               = TRUE,
          processing_status       = "excluded_by_date",
          pagination_group_status = "aborted"
        )]
      }
    }
  }
  
  # dissolve any valid_up / valid_down group that contains a SitemapIndex

  valid_grps <- unique(
    step_7_progression_dt[pagination_group_status %in% c("valid_up", "valid_down")]$pagination_group
  )
  
  for (g in valid_grps) {
    rows_g <- step_7_progression_dt[pagination_group == g]
    if (any(rows_g$root_tag == "sitemapindex")) {
  
      diss_idx <- which(step_7_progression_dt$pagination_group == g &
                        !step_7_progression_dt$processing_status %in% err_vec)
  
      if (length(diss_idx) > 0) {
        step_7_progression_dt[diss_idx, `:=`(
          processed               = FALSE,
          processing_status       = "in_progress",
          pagination_group_status = "dissolved",
          pagination_group        = NA_character_,
          pagination_index        = NA_integer_
        )]
      }
    }
  }
  
  assign(step_7_progression_dt_name, step_7_progression_dt, envir = .GlobalEnv)
}

# Function: step_7_2_master_dt_update_func
# This function updates or inserts entries into the global_master_dt table.
# Status assignment logic is extended to cover new blocked/retry-related categories.

step_7_2_master_dt_update_func <- function(
  domain_id,
  domain_url,
  l1_id, 
  layer_1_url,
  request_increment = 0L,
  current_user_agent_id = NA_integer_
) {
  # Load related tables
  prog_name   <- paste0("sitemap_id_", l1_id, "_progression_dt")
  log_name    <- paste0("sitemap_id_", l1_id, "_response_log_dt")
  output_name <- paste0("sitemap_id_", l1_id, "_output_dt")
  
  progression_dt <- if (exists(prog_name, envir = .GlobalEnv))
    get(prog_name, envir = .GlobalEnv) else data.table()
  response_log_dt <- if (exists(log_name, envir = .GlobalEnv))
    get(log_name, envir = .GlobalEnv) else data.table()
  output_dt <- if (exists(output_name, envir = .GlobalEnv))
    get(output_name, envir = .GlobalEnv) else data.table()

  # Determine input_processing_status based on progression statuses
  status_vals <- unique(na.omit(progression_dt$processing_status))
  only_final <- all(status_vals %in% c("excluded_by_string", "excluded_by_date", "scraped", "all_child_links_processed", 
                                       "response_error", "xml_error", "parse_error", "unsupported_root_tag" ,"all_processed_some_errors"))
  only_error <- all(status_vals %in% c("response_error", "xml_error", "parse_error", "unsupported_root_tag"))
  has_final  <- any(status_vals %in% c("excluded_by_string", "excluded_by_date", "scraped", "all_child_links_processed"))
  has_active <- any(status_vals %in% c("in_progress", "subsitemap_sorted"))

  if (has_active) {
    input_status <- "in_progress"
  } else if (only_final) {
    input_status <- "fully_processed"
  } else if (only_error && !has_final) {
    input_status <- "total_error"
  } else {
    input_status <- "in_progress"
  }

  # Determine processing_flag from last action in response log
  if (nrow(response_log_dt) > 0) {
    actions <- na.omit(response_log_dt$action_taken)
    last_action <- if (length(actions) > 0) actions[length(actions)] else NA_character_
    processing_flag <- switch(
      last_action,
      logged              = "normal",
      soft_block_handling = "softblock",
      hard_block          = "retry",
      "normal"
    )
  } else {
    processing_flag <- "normal"
  }

  # Compute totals
  slice <- global_master_dt[layer_1_url_id == l1_id, total_request_count]

  total_requests_prior <- if (length(slice) == 0) 0L else slice[1]
  total_requests_new   <- total_requests_prior + as.integer(request_increment)
  total_urlsets        <- nrow(output_dt)

  # Update or insert master_dt row
  if (l1_id %in% global_master_dt$layer_1_url_id) {
    global_master_dt[layer_1_url_id == l1_id, `:=`(
        input_processing_status = input_status,
        total_request_count     = total_requests_new,
        total_urlsets_scraped   = total_urlsets,
        last_checked            = Sys.time(),
        current_user_agent_id   = current_user_agent_id,
        processing_flag         = processing_flag
      )]
  } else {
    global_master_dt <<- rbind(
      global_master_dt,
      data.table(
        domain_id               = domain_id,
        layer_1_url_id          = l1_id,
        layer_1_url             = layer_1_url,
        input_processing_status = input_status,
        total_request_count     = total_requests_new,
        total_urlsets_scraped   = total_urlsets,
        last_checked            = Sys.time(),
        current_user_agent_id   = current_user_agent_id,
        processing_flag         = processing_flag
      ),
      fill = TRUE
    )
  }
  
  # Checking fully processed inputs for retry flags and labeling for retry if neccessary.
  fully_processed_rows <- global_master_dt[input_processing_status == "fully_processed"]

  for (i in seq_len(nrow(fully_processed_rows))) {
    l1_id_check <- fully_processed_rows$layer_1_url_id[i]
    log_name_check <- paste0("sitemap_id_", l1_id_check, "_response_log_dt")

    if (exists(log_name_check, envir = .GlobalEnv)) {
      log_dt_check <- get(log_name_check, envir = .GlobalEnv)
      if ("retry_flag" %in% names(log_dt_check) && any(log_dt_check$retry_flag == TRUE, na.rm = TRUE)) {
        global_master_dt[layer_1_url_id == l1_id_check, input_processing_status := "partially_processed_and_moved_to_retry"]
      }
    }
  }
  
}

# Function: step_7_3_response_log_update_func
# This function logs all non-200 HTTP responses and updates category counters and flags.
# After logging, it updates the associated progression entry and resets counters if needed.

step_7_3_response_log_update_func <- function(
  domain_id,
  domain_url,
  layer_1_url_id,
  layer_1_url,
  requested_url_id,
  requested_url,
  client_profile_id,
  http_response
) {
  # Construct the name of the response-log data.table for this sitemap
  resp_log_name <- paste0("sitemap_id_", layer_1_url_id, "_response_log_dt")

  # If the response-log table does not exist yet, create it with the required columns
  if (!exists(resp_log_name, envir = .GlobalEnv)) {
    assign(resp_log_name, data.table(
      domain_id                  = integer(),
      domain_url                 = character(),
      layer_1_url_id             = integer(),
      layer_1_url                = character(),
      requested_url_id           = integer(),
      requested_url              = character(),
      client_profile_id          = integer(),
      timestamp                  = as.POSIXct(character()),
      http_status_code           = integer(),
      http_status_message        = character(),
      response_header_snippet    = character(),
      response_body_snippet      = character(),
      response_category          = character(),
      soft_block_count_at_time   = integer(),
      hard_block_count_at_time   = integer(),
      other_error_count_at_time  = integer(),
      action_taken               = character(),
      retry_flag                 = logical()
    ), envir = .GlobalEnv)
  }

  # Load the existing response-log table
  resp_log_dt <- get(resp_log_name, envir = .GlobalEnv)

  # Initialize local variables for logging
  if (is.null(http_response)) {
    # No response object → treat as hard block
    status_code     <- NA_integer_
    status_message  <- "NULL_response"
    header_snip     <- "NULL"
    body_snip       <- "NULL"
    category        <- "hard_block_indication"
  } else {
    # Extract HTTP status code
    status_code    <- httr::status_code(http_response)

    # Safely obtain a human-readable status message
    status_info    <- httr::http_status(http_response)
    status_message <- status_info$reason

    # Capture first 2000 characters of headers and body
    header_snip <- paste0(
      capture.output(str(httr::headers(http_response))),
      collapse = "\n"
    )
    header_snip <- substr(header_snip, 1, 2000)

    body_snip <- tryCatch(
      rawToChar(httr::content(http_response, as = "raw")),
      error = function(e) "ERROR_READING_BODY"
    )
    body_snip <- substr(body_snip, 1, 2000)

    # Classify response category
    if (is.na(status_code) || status_code %in% c(401, 403, 407)) {
      category <- "hard_block_indication"
    } else if (status_code %in% c(406, 408, 429, 503)) {
      category <- "soft_block_indication"
    } else {
      category <- "other_error"
    }
  }

  retry_flag_value <- if (category == "other_error") FALSE else TRUE
  
  # Retrieve previous counters from the last log entry
  prev_soft  <- 0L
  prev_hard  <- 0L
  prev_other <- 0L
  if (nrow(resp_log_dt) > 0) {
    last_cat <- tail(na.omit(resp_log_dt$response_category), 1)
    if (length(last_cat) == 1) {
      if (last_cat == "soft_block_indication") {
        prev_soft <- tail(resp_log_dt$soft_block_count_at_time, 1)
      } else if (last_cat == "hard_block_indication") {
        prev_hard <- tail(resp_log_dt$hard_block_count_at_time, 1)
      } else if (last_cat == "other_error") {
        prev_other <- tail(resp_log_dt$other_error_count_at_time, 1)
      }
    }
  }

  # Increment or reset counters based on current category
  soft_count  <- if (category == "soft_block_indication") prev_soft + 1L else 0L
  hard_count  <- if (category == "hard_block_indication") prev_hard + 1L else 0L
  other_count <- if (category == "other_error") prev_other + 1L else 0L

  # Decide action based on thresholds
  action <- "logged"
  if (soft_count > 10L) {
    action <- "soft_block_handling"
  } else if (hard_count > 10L || other_count > 10L) {
    action <- "hard_block"
  }

  # Build a new log entry
  new_entry <- data.table(
    Domain_id                  = domain_id,
    Domain_url                 = domain_url,
    Layer_1_url_id             = layer_1_url_id,
    Layer_1_url                = layer_1_url,
    requested_url_id           = requested_url_id,
    requested_url              = requested_url,
    client_profile_id          = client_profile_id,
    timestamp                  = Sys.time(),
    http_status_code           = status_code,
    http_status_message        = status_message,
    response_header_snippet    = header_snip,
    response_body_snippet      = body_snip,
    response_category          = category,
    soft_block_count_at_time   = soft_count,
    hard_block_count_at_time   = hard_count,
    other_error_count_at_time  = other_count,
    action_taken               = action,
    retry_flag                 = retry_flag_value
  )

  # Append the new entry and save back to the global environment
  resp_log_dt <- rbind(resp_log_dt, new_entry, fill = TRUE)
  assign(resp_log_name, resp_log_dt, envir = .GlobalEnv)

  # Update the progression table for this failed URL
  prog_name <- paste0("sitemap_id_", layer_1_url_id, "_progression_dt")
  if (exists(prog_name, envir = .GlobalEnv)) {
    dt  <- get(prog_name, envir = .GlobalEnv)
    idx <- which(dt$current_url_id == requested_url_id)
    if (length(idx) > 0) {
      data.table::set(dt, i = idx, j = "processed",         value = FALSE)
      data.table::set(dt, i = idx, j = "processing_status", value = "response_error")
    }
    assign(prog_name, dt, envir = .GlobalEnv)
  }
}

# Function: step_7_4_urlset_scraper_func
# parses the XML, checks lastmod tags, and stores valid URLSETs in the output data table.
# Ensures uniqueness of urlset entries and ids.
# Updated step_7_4_urlset_scraper_func with pagination-group date_before_range logic,
# preserving existing progression values except for group-status override.
step_7_4_urlset_scraper_func <- function(
  url,
  http_response,
  xml_doc = NULL,
  global_date_start,
  global_date_end,
  domain_id,
  domain_url,
  layer_1_url_id,
  layer_1_url,
  current_url_id,
  parent_url_id
) {
  # Parse XML from response or provided doc
  if (!is.null(xml_doc)) {
    doc <- xml_doc
  } else {
    doc <- NULL
    if (grepl("\\.gz$", url, ignore.case = TRUE)) {
      raw <- tryCatch(httr::content(http_response, as = "raw"), error = function(e) NULL)
      if (!is.null(raw)) {
        con <- tryCatch(gzcon(rawConnection(raw, "rb")), error = function(e) NULL)
        if (!is.null(con)) {
          doc <- tryCatch(xml2::read_xml(con), error = function(e) NULL)
          close(con)
        }
      }
    } else {
      txt <- tryCatch(httr::content(http_response, as = "text", encoding = "UTF-8"), error = function(e) NULL)
      if (!is.null(txt)) {
        doc <- tryCatch(xml2::read_xml(txt), error = function(e) NULL)
      }
    }
  }

  # If parsing failed, log error and update progression
  if (is.null(doc)) {
    global_error_dt <<- rbind(
      global_error_dt,
      data.table(
        domain_id = domain_id, domain_url = domain_url,
        layer_1_url_id = layer_1_url_id, layer_1_url = layer_1_url,
        error_url_id = current_url_id, error_url = url,
        parent_url_id = parent_url_id, root_tag = "urlset",
        error_category = "xml_parse_error",
        processed_flag = FALSE, retry_flag = TRUE,
        timestamp = Sys.time(), source_function = "step_7_4_urlset_scraper_func",
        status_code = httr::status_code(http_response)
      ), fill = TRUE
    )
    step_7_1_progression_update(
      domain_id = domain_id, domain_url = domain_url,
      layer_1_url_id = layer_1_url_id, layer_1_url = layer_1_url,
      current_url = url, parent_url_id = parent_url_id,
      processed = FALSE, processing_status = "xml_error",
      in_range = "unknown", root_tag = "urlset"
    )
    return(NULL)
  }

  # Ensure root tag is <urlset>
  if (tolower(xml2::xml_name(xml2::xml_root(doc))) != "urlset") {
    return(NULL)
  }

  # Normalize namespace
  ns_map <- xml2::xml_ns_rename(xml2::xml_ns(doc), d1 = "ns")

  # run date check 
  step_7_4_date_res <- step_5_1_date_check_urlset_func(
    xml_doc   = doc,
    ns_map    = ns_map,
    date_from = global_date_start,
    date_to   = global_date_end
  )
  # Extract all <lastmod> dates
  locs  <- xml2::xml_find_all(doc, ".//ns:loc", ns = ns_map)
  lastmods <- xml2::xml_find_all(doc, ".//ns:lastmod", ns = ns_map) |> xml2::xml_text()
  dates <- as.Date(gsub("T.*","", lastmods), "%Y-%m-%d")
  dates <- dates[!is.na(dates)]

  # fetch old progression values once
  prog_name <- paste0("sitemap_id_", layer_1_url_id, "_progression_dt")
  prog_dt   <- get(prog_name, envir = .GlobalEnv)
  old_row <- prog_dt[current_url == url][1] 
  
  # pagination‐group date_before_range check
  if (!is.na(old_row$pagination_group) && length(dates) > 0) {

  url_from  <- min(dates)
  url_to    <- max(dates)

   
    if (url_to < global_date_start) {
      step_7_1_progression_update(
        domain_id               = domain_id,
        domain_url              = domain_url,
        layer_1_url_id          = layer_1_url_id,
        layer_1_url             = layer_1_url,
        current_url             = url,
        parent_url_id           = parent_url_id,
        processed               = TRUE,                 
        processing_status       = "excluded_by_date",  
        in_range                = "no",
        root_tag                = "urlset",
        subsitemap_status       = "not_a_sitemap",
        sort_order              = list(data.table()),
        subsitemap_progress     = "not_a_sitemap",
        pagination_group        = old_row$pagination_group,
        pagination_index        = old_row$pagination_index,
        pagination_group_status = "date_before_range"
      )
      return(NULL)
    }
  }

  # Call original date-check for output
  date_info <- step_5_1_date_check_urlset_func(doc, ns_map, global_date_start, global_date_end)
  link_count <- length(xml2::xml_find_all(doc, ".//ns:loc", ns = ns_map))
  date_range <- NA_character_
  if (date_info$reason == "in_range") {
    rd <- dates[dates >= global_date_start & dates <= global_date_end]
    if (length(rd) > 0) {
      date_range <- paste0(format(min(rd), "%Y-%m-%d"), " - ", format(max(rd), "%Y-%m-%d"))
    }
  }

  # Write to output table if proceed
  if (date_info$decision == "proceed") {
    out_name <- paste0("sitemap_id_", layer_1_url_id, "_output_dt")
    if (!exists(out_name, envir = .GlobalEnv)) {
      assign(out_name, data.table(
        domain_id = integer(), domain_url = character(),
        layer_1_url_id = integer(), layer_1_url = character(),
        urlset_id = integer(), urlset_url = character(),
        in_range = character(), urlset_link_count = integer(),
        urlset_date_range = character(), urlset_content = character()
      ), envir = .GlobalEnv)
    }
    out_dt <- get(out_name, envir = .GlobalEnv)
    new_id <- if (nrow(out_dt)==0) 1L else max(out_dt$urlset_id)+1L
    out_dt <- rbind(out_dt, data.table(
      domain_id = domain_id, domain_url = domain_url,
      layer_1_url_id = layer_1_url_id, layer_1_url = layer_1_url,
      urlset_id = new_id, urlset_url = url,
      in_range = date_info$reason,
      urlset_link_count = link_count,
      urlset_date_range = date_range,
      urlset_content = as.character(doc)
    ), fill=TRUE)
    assign(out_name, out_dt, envir = .GlobalEnv)
  }

  # Final progression update preserving original pagination_group/index
  step_7_1_progression_update(
    domain_id           = domain_id,
    domain_url          = domain_url,
    layer_1_url_id      = layer_1_url_id,
    layer_1_url         = layer_1_url,
    current_url         = url,
    parent_url_id       = parent_url_id,
    processed           = TRUE,
    processing_status   = switch(
      step_7_4_date_res$reason,
      in_range         = "scraped",
      no_lastmod_found = "scraped",
      "excluded_by_date"
    ),
    in_range            = step_7_4_date_res$reason,
    root_tag            = "urlset",
    subsitemap_status   = "not_a_sitemap",
    sort_order          = list(data.table()),
    subsitemap_progress = "not_a_sitemap",
    pagination_group    = old_row$pagination_group,
    pagination_index    = old_row$pagination_index
  )
  
  # return summary
  list(
    in_range  = (step_7_4_date_res$decision=="proceed" && step_7_4_date_res$reason=="in_range"),
    reason    = step_7_4_date_res$reason,
    link_cnt  = length(locs),
    date_span = if (length(dates)>0) paste0(min(dates)," - ",max(dates)) else NA_character_
  )
}


cat("Step 7 completed: Progression_dt updater function, response_dt updater function, master_dt updater function, urlset scraper function initialized.\n")

```

## Code Chunk 8: Main Recursive Sitemap Processing Function with Logging

### Summary:

This code segment defines the primary recursive engine for sitemap processing. The function orchestrates sitemap traversal by dynamically managing HTTP requests, XML parsing, status logging, and conditional branching based on the content structure (`urlset`, `sitemapindex`, or unsupported types). The function integrates deeply with progression tracking and error logging mechanisms established in earlier steps. The core logic includes validation of pagination groups, conditional execution based on request limits and error thresholds, and stateful control over retry behavior and user-agent rotation.

Inputs include metadata from the `global_master_dt` table and all relevant processing tables derived from the current `layer_1_url`. The function outputs updated state across `progression_dt`, `master_dt`, `response_log_dt`, and `output_dt`, as well as detailed print logs for progress tracking.

#### Function: `step_8_recursive_processing_func`

This is the central recursive function that governs the iterative processing of sitemap URLs. It performs the following:
- Retrieves relevant metadata and initializes counters.
- Validates candidate pagination groups by sampling child links and determining date regularity.
- Iteratively processes links by priority (non-paginated first), applying a maximum request and error threshold.
- For each URL, it executes an HTTP GET request and handles XML parsing, classifying results as valid `urlset`, `sitemapindex`, or unsupported.
- Depending on the root tag, it calls specialized handlers: `step_7_4_urlset_scraper_func` for URLSETs or `step_6_sorting_func` for sitemap indexes.
- It logs all non-200 responses, updates all global tracking tables, and prints iteration summaries.

The function is both depth- and state-aware and ensures robust processing by integrating internal retry logic, error handling, and grouped pagination validation via `step_8_2_validate_pagination_group`. Upon completion or failure conditions, it finalizes the update cycle via `step_8_1_finish_func`.

#### Function: `step_8_1_finish_func`

This internal helper finalizes the processing cycle. It recalculates the `progression_dt` entry for the root URL and triggers a master update via `step_7_2_master_dt_update_func`. It also outputs summary statistics to the console: request counts, total processed entries, scraped URLSETs, and error statistics.

#### Function: `step_8_2_validate_pagination_group`

This validation subroutine samples three entries from a pagination group (first, middle, last) and examines their `<lastmod>` tags to assess temporal monotonicity. It flags the group as `"valid_up"`, `"valid_down"`, or `"invalid"` depending on the date trend. If any of the sample responses are not valid `urlset` XMLs, the group is dissolved.

```{r Step 8: Main recursive sitemap processing function with logging}

# Actual recursive function 
step_8_recursive_processing_func <- function(next_input) {
  # get master‑row + basics
  master_row  <- global_master_dt[next_input]
  did         <- master_row$domain_id
  dur         <- master_row$domain_url
  lid         <- master_row$layer_1_url_id
  lurl        <- master_row$layer_1_url
  flag        <- master_row$processing_flag
  cur_ua_id   <- master_row$current_user_agent_id
  cur_ua_id <- global_master_dt$`current_user_agent_id`[next_input]
  if (is.na(cur_ua_id) || cur_ua_id == 0 || is.null(cur_ua_id)) {
    cur_ua_id <- 2L  
  } else {
    cur_ua_id <- (cur_ua_id %% length(global_user_agent_list)) + 1L
  }
  ua_string   <- global_user_agent_list[cur_ua_id]
  global_master_dt[next_input, current_user_agent_id := cur_ua_id]

  max_req     <- ifelse(flag == "softblock", 15L, 20L)
  sleep_delay <- ifelse(flag == "softblock", 3, 0)

  # local tables
  prog_name <- paste0("sitemap_id_", lid, "_progression_dt")
  out_name  <- paste0("sitemap_id_", lid, "_output_dt")
  log_name  <- paste0("sitemap_id_", lid, "_response_log_dt")
  prog_dt   <- get(prog_name, envir = .GlobalEnv)
  out_dt    <- get(out_name,  envir = .GlobalEnv)
  log_dt    <- get(log_name,  envir = .GlobalEnv)
  prog_root <- prog_dt[current_url_id == 1L]

  # initialize counters
  internal_request_counter <- 0L
  internal_error_counter   <- 0L

  ## Helper to refresh all controll structures 
  step_8_1_finish_func <- function() {
  # recalc progression (forces progress string etc.)
  if (exists(prog_name, envir = .GlobalEnv)) {
    dt  <- get(prog_name, envir = .GlobalEnv)
    root_idx <- which(dt$current_url == lurl & dt$parent_url_id == 0L)
    if (length(root_idx) > 0) {
      # get existing vlaues 
      proc_val   <- dt$processed[root_idx][1]
      status_val <- dt$processing_status[root_idx][1]
      in_range_val <- dt$in_range[root_idx][1]
      
      # Progression update 
      step_7_1_progression_update(
        domain_id         = did,
        domain_url        = dur,
        layer_1_url_id    = lid,
        layer_1_url       = lurl,
        current_url       = lurl,
        parent_url_id     = 0L,
        processed         = proc_val,
        processing_status = status_val, 
        in_range          = in_range_val 
      )
    }
  }

  # Master-Update
  step_7_2_master_dt_update_func(
    domain_id             = did,
    domain_url            = dur,
    l1_id                 = lid,
    layer_1_url           = lurl,
    request_increment     = internal_request_counter,
    current_user_agent_id = cur_ua_id
  )

  # Summary Print
  out_dt <- get(out_name, envir = .GlobalEnv)
  total_processed <- sum(prog_dt$processed, na.rm = TRUE)
  total_errors    <- sum(prog_dt$processing_status %in%
                       c("response_error", "xml_error", "unsupported_root_tag"), na.rm = TRUE)

  cat(sprintf("Requests sent to %s in this iteration: %d.\n", lurl, internal_request_counter))
  cat(sprintf("Total requests: %d.\n", global_master_dt[layer_1_url_id == lid]$total_request_count))
  cat(sprintf("Total urlsets scraped: %d.\n", nrow(out_dt)))
  cat(sprintf("Total progression entries: %d.\n", nrow(prog_dt)))
  cat(sprintf("Total links processed: %d.\n", total_processed))
  cat(sprintf("Total errors: %d.\n", total_errors))
  cat(sprintf("State of input sitemap: %s.\n", global_master_dt[layer_1_url_id == lid]$processing_flag))
  }

  ## Helper to validate groups in line 
  step_8_2_validate_pagination_group <- function(layer_1_url_id, group_id, global_date_start, global_date_end) {
  prog_name <- paste0("sitemap_id_", layer_1_url_id, "_progression_dt")
  prog_dt <- get(prog_name, envir = .GlobalEnv)

  # Identify rows belonging to this pagination group
  group_rows <- prog_dt[pagination_group == group_id]

  # Sample three URLs: first, middle, last
  sample_idx <- c(1, ceiling(nrow(group_rows) / 2), nrow(group_rows))
  detected_dates <- c()
  sample_tags <- c()
  for (i in sample_idx) {
    test_url <- group_rows$current_url[i]
    resp <- tryCatch(
      httr::GET(test_url, httr::user_agent(global_user_agent_list[2]), httr::timeout(30)),
      error = function(e) NULL
    )
    if (!is.null(resp) && httr::status_code(resp) == 200L) {
      xml_doc <- tryCatch(
        xml2::read_xml(httr::content(resp, as = "text", encoding = "UTF-8")),
        error = function(e) NULL
      )
      root_tag <- tolower(xml2::xml_name(xml2::xml_root(xml_doc)))
      sample_tags <- c(sample_tags, root_tag)
      if (root_tag == "urlset") {
        ns_map <- xml2::xml_ns_rename(xml2::xml_ns(xml_doc), d1 = "ns")
        date_res <- step_5_1_date_check_urlset_func(
          xml_doc   = xml_doc,
          ns_map    = ns_map,
          date_from = global_date_start,
          date_to   = global_date_end
        )
        
        if (root_tag == "urlset") {
        ns_map <- xml2::xml_ns_rename(xml2::xml_ns(xml_doc), d1 = "ns")
        lastmods <- xml2::xml_find_all(xml_doc, ".//ns:lastmod", ns = ns_map) |> xml2::xml_text()
        dates <- as.Date(gsub("T.*", "", lastmods), format = "%Y-%m-%d")
        dates <- dates[!is.na(dates)]
        
        if (length(dates) > 0) {
          detected_dates <- c(detected_dates, min(dates))  
        
        } else {
          cat(sprintf("%s No valid last mod tags found in sample request.\n", test_url))
        }
      }
      }
    }
  }

  # If any sample is not a urlset, dissolve group
  if (!(length(sample_tags) == 3 && all(sample_tags == "urlset"))) {
    for (url in group_rows$current_url) {
      step_7_1_progression_update(
        domain_id                = group_rows$domain_id[1],
        domain_url               = group_rows$domain_url[1],
        layer_1_url_id           = layer_1_url_id,
        layer_1_url              = group_rows$layer_1_url[1],
        current_url              = url,
        parent_url_id            = group_rows$parent_url_id[1],
        pagination_group         = NA_character_,
        pagination_index         = NA_integer_,
        pagination_group_status  = "invalid_urlsets"
      )
    }
    return(FALSE)
  }

  # Check if dates are monotonic within 2-day tolerance
  is_up   <- all(detected_dates[-1] >= detected_dates[-length(detected_dates)] - 2)
  is_down <- all(detected_dates[-1] <= detected_dates[-length(detected_dates)] + 2)
  status_to_set <- if (is_up) "valid_up" else if (is_down) "valid_down" else "invalid"

  # Apply status updates for entire group
  for (url in group_rows$current_url) {
    if (status_to_set == "invalid") {
      step_7_1_progression_update(
        domain_id               = group_rows$domain_id[1],
        domain_url              = group_rows$domain_url[1],
        layer_1_url_id          = layer_1_url_id,
        layer_1_url             = group_rows$layer_1_url[1],
        current_url             = url,
        parent_url_id           = group_rows$parent_url_id[1],
        pagination_group_status = "invalid",
        pagination_group        = NA_character_,
        pagination_index        = NA_integer_
      )
    } else {
      step_7_1_progression_update(
        domain_id               = group_rows$domain_id[1],
        domain_url              = group_rows$domain_url[1],
        layer_1_url_id          = layer_1_url_id,
        layer_1_url             = group_rows$layer_1_url[1],
        current_url             = url,
        parent_url_id           = group_rows$parent_url_id[1],
        pagination_group_status = status_to_set
      )
    }
  }
  return(status_to_set %in% c("valid_up", "valid_down"))
}

  # recursion 
  repeat {
     
    # abort check
    if (internal_request_counter >= max_req || internal_error_counter >= 5L) {
      step_8_1_finish_func(); break
    }
    
    # check for "candidate" groups 
    candidate_groups <- unique(prog_dt[pagination_group_status == "candidate"]$pagination_group)
    for (g in candidate_groups) {
      step_8_2_validate_pagination_group(layer_1_url_id = lid,
                                 group_id = g,
                                 global_date_start = global_date_start,
                                 global_date_end = global_date_end)
      internal_request_counter <- internal_request_counter + 3L
    }
    
    # reload progression each loop
    prog_dt <- get(prog_name, envir = .GlobalEnv)
    if (!"pagination_group_status" %in% colnames(prog_dt)) {
      prog_dt[, pagination_group_status := NA_character_]
      assign(prog_name, prog_dt, envir = .GlobalEnv)
    }
    
    # filter out errors 
    valid_dt <- prog_dt[
      !processing_status %in% c("xml_error", "response_error", "unsupported_root_tag") &
      processed == FALSE &
      (is.na(root_tag) | root_tag == "unknown")
    ]
    
    # first: no pagination
    group_a <- valid_dt[is.na(pagination_group) & is.na(pagination_index)]
    if (nrow(group_a) > 0) {
      next_row <- group_a[order(parent_url_id, sort_place, current_url_id)][1]
    } else {
      # then: paginated
      group_b <- valid_dt[!is.na(pagination_group) & !is.na(pagination_index)]
      if (nrow(group_b) > 0) {
        next_row <- group_b[
          order(parent_url_id, pagination_group, pagination_index, current_url_id)
        ][1]
      } else {
        next_row <- NULL
      }
    }
    
    # break if all done 
    if (is.null(next_row) || nrow(next_row) == 0) {
      step_8_1_finish_func()
      break
    }
    
    # GET request
    resp <- tryCatch(
      httr::GET(next_row$current_url,
                httr::user_agent(ua_string),
                httr::timeout(30)),
      error = function(e) NULL
    )
    internal_request_counter <- internal_request_counter + 1L

    Sys.sleep(sleep_delay)

    # response handling 
    if (!is.null(resp) && httr::status_code(resp) == 200L) {
      # reset block counters in response_log
      if (exists(log_name, envir = .GlobalEnv)) {
        tmp_log <- get(log_name, envir = .GlobalEnv)
        tmp_log[, c(
          "soft_block_count_at_time",
          "hard_block_count_at_time",
          "other_error_count_at_time"
        ) := .(0L, 0L, 0L)]
        assign(log_name, tmp_log, envir = .GlobalEnv)
      }
      internal_error_counter <- 0L
    } else {
      # non‑200
      step_7_3_response_log_update_func(
        domain_id         = did,
        domain_url        = dur,
        layer_1_url_id    = lid,
        layer_1_url       = lurl,
        requested_url_id  = next_row$current_url_id,
        requested_url     = next_row$current_url,
        client_profile_id = cur_ua_id,
        http_response     = resp
      )
      # progression flag
      step_7_1_progression_update(
        domain_id         = did, domain_url = dur,
        layer_1_url_id    = lid, layer_1_url = lurl,
        current_url       = next_row$current_url,
        parent_url_id     = next_row$parent_url_id,
        processed         = FALSE,
        processing_status = "response_error"
      )
      internal_error_counter <- internal_error_counter + 1L
      cat(sprintf(
        "Error response for link: %s. \n Status code %s. \n Entry in response_log made.\n",
        next_row$current_url,
        ifelse(is.null(resp), "NULL", httr::status_code(resp))
      ))
      next
    }
  
    # gz handling
    xml_doc <- NULL
    
    if (grepl("\\.gz$", next_row$current_url, ignore.case = TRUE)) {
      # 1) raw data as vector
      raw_data <- tryCatch(httr::content(resp, as = "raw"),
                           error = function(e) NULL)
      if (!is.null(raw_data)) {
        # 2) unapck binary
        con_gz <- tryCatch(gzcon(rawConnection(raw_data, "rb")),
                           error = function(e) NULL)
        if (!is.null(con_gz)) {
          # 3) parse connection
          xml_doc <- tryCatch(xml2::read_xml(con_gz),
                              error = function(e) NULL)
          close(con_gz)
        }
      }
    } else {
      # normal xml
      xml_text <- tryCatch(httr::content(resp, as = "text", encoding = "UTF-8"),
                           error = function(e) NULL)
      if (!is.null(xml_text)) {
        xml_doc <- tryCatch(xml2::read_xml(xml_text),
                            error = function(e) NULL)
      }
    }
    
    if (is.null(xml_doc)) {
      # parse error
      global_error_dt <<- rbind(
        global_error_dt,
        data.table::data.table(
          domain_id = did, domain_url = dur,
          layer_1_url_id = lid, layer_1_url = lurl,
          error_url_id = next_row$current_url_id,
          error_url = next_row$current_url,
          parent_url_id = next_row$parent_url_id,
          root_tag = NA_character_,
          error_category = "xml_parse_error",
          processed_flag = FALSE,
          retry_flag = TRUE,
          timestamp = Sys.time(),
          source_function = "step_8_recursive_processing_func",
          status_code = httr::status_code(resp)
        ),
        fill = TRUE
      )
      step_7_1_progression_update(
        domain_id = did, domain_url = dur,
        layer_1_url_id = lid, layer_1_url = lurl,
        current_url = next_row$current_url,
        parent_url_id = next_row$parent_url_id,
        processed = FALSE,
        processing_status = "xml_error"
      )
      cat(sprintf(
        "Error in link %s. Link moved to error_dt, reason: parse_error.\n",
        next_row$current_url
      ))
      next
    }

    # root tag routing
    rtag <- tolower(xml2::xml_name(xml2::xml_root(xml_doc)))
    if (!rtag %in% c("urlset", "sitemapindex", "sitemap")) {
      global_error_dt <<- rbind(
        global_error_dt,
        data.table::data.table(
          domain_id = did, domain_url = dur,
          layer_1_url_id = lid, layer_1_url = lurl,
          error_url_id = next_row$current_url_id,
          error_url = next_row$current_url,
          parent_url_id = next_row$parent_url_id,
          root_tag = rtag,
          error_category = "unsupported_root_tag",
          processed_flag = FALSE,
          retry_flag = TRUE,
          timestamp = Sys.time(),
          source_function = "step_8_recursive_processing_func",
          status_code = httr::status_code(resp)
        ),
        fill = TRUE
      )
      step_7_1_progression_update(
        domain_id = did, domain_url = dur,
        layer_1_url_id = lid, layer_1_url = lurl,
        current_url = next_row$current_url,
        parent_url_id = next_row$parent_url_id,
        processed = FALSE,
        processing_status = "unsupported_root_tag"
      )
      cat(sprintf(
        "Error in link %s. Link moved to error_dt, reason: unsupported_root_tag.\n",
        next_row$current_url
      ))
      next
    }

    if (rtag == "urlset") {
    # call urlset scraping function 
    step_7_4_res <- step_7_4_urlset_scraper_func(
      url               = next_row$current_url,
      http_response     = resp,
      xml_doc           = xml_doc,
      global_date_start = global_date_start,
      global_date_end   = global_date_end,
      domain_id         = did,
      domain_url        = dur,
      layer_1_url_id    = lid,
      layer_1_url       = lurl,
      current_url_id    = next_row$current_url_id,
      parent_url_id     = next_row$parent_url_id
    )
  
    } else if (rtag == "sitemapindex") {
      # collect child links
      ns_map <- xml2::xml_ns_rename(xml2::xml_ns(xml_doc), d1 = "ns")
      child_links <- xml2::xml_find_all(xml_doc, ".//ns:loc",
                                        ns = ns_map) %>% xml2::xml_text()

      sort_dt <- step_6_sorting_func(
        step_6_links_vector       = child_links,
        layer_1_url_id            = lid,
        layer_1_url               = lurl,  
        parent_url                = next_row$current_url,
        parent_url_id             = next_row$current_url_id,
        global_date_start         = global_date_start,
        global_date_end           = global_date_end,
        global_excluded_strings   = global_excluded_strings,
        domain_id                 = did,
        domain_url                = dur
      )
      
      step_7_1_progression_update(
        domain_id         = did,      domain_url  = dur,
        layer_1_url_id    = lid,      layer_1_url = lurl,
        current_url       = next_row$current_url,
        parent_url_id     = next_row$parent_url_id,
        processed         = FALSE,
        processing_status = "subsitemap_sorted",
        root_tag          = "sitemapindex",
        subsitemap_status = "in_progress"
      )

      # summary print 
      n_total <- nrow(sort_dt)
      n_valid <- sum(sort_dt$sorted == "yes")
      n_ruled <- n_total - n_valid
      
      cat(sprintf("Sub-sitemap URL: %s \n", next_row$current_url))
      cat(sprintf("Total links detected on subsitemap: %d \n", n_total))
      cat(sprintf("Excluded links: %d \n", n_ruled))
      cat(sprintf("Valid links: %d \n", n_valid))
    }
  }
}


cat("Step 8 completed: Recursive sitemap processing function defined.\n")

```

## Code Chunk 9: Defining the Master Loop

### Summary:

This code defines a global orchestration function that governs the lifecycle of sitemap processing. Acting as a high-level execution loop, it repeatedly invokes the recursive processing function on all pending sitemap entries, ensuring that every item in `global_master_dt` is either processed, retried, or definitively marked as failed. The loop incorporates status-based filtering and structured error handling to maintain process resilience and ensure full pipeline coverage.

The input is the global data table `global_master_dt`, from which it identifies all entries not yet completed. The output is a fully updated state across all involved structures (`progression_dt`, `response_log_dt`, `output_dt`, and `global_master_dt`) once the loop terminates.

#### Function: `step_9_master_loop_func`

This function performs the following key operations:

- Initializes an iteration counter and begins a `repeat` loop that terminates only when all input entries have reached a terminal state.
- In each iteration, it identifies entries with a processing status not in the set `{"fully_processed", "partially_processed_and_moved_to_retry", "total_error"}`.
- For each such index, it safely invokes the `step_8_recursive_processing_func` within a `tryCatch` block to prevent premature termination in case of error.
- After processing, it logs summary statistics including counts for fully processed, partially failed, totally failed, and still-active entries.
- When no entries remain pending, the loop exits and prints a final status report.

This function ensures robustness by encapsulating lower-level processing logic in a controlled retry-capable master flow and is critical for executing the full scraping and logging cycle across multiple input domains.

```{r Step 9: Defining the Master Loop }
# Define a master loop that processes all pending entries until completion
step_9_master_loop_func <- function() {
  step_9_iter_count <- 0L
  
  repeat {
    # Identify indices still in progress
    step_9_pending_idx <- which(
      ! global_master_dt$input_processing_status %in% 
        c("partially_processed_and_moved_to_retry", "fully_processed", "total_error")
    )
    
    # Exit loop when no pending entries remain
    if (length(step_9_pending_idx) == 0L) break
    
    step_9_iter_count <- step_9_iter_count + 1L
    
    # Process each pending entry, catching errors to avoid aborting
    for (step_9_idx in step_9_pending_idx) {
      tryCatch(
        {
          step_8_recursive_processing_func(next_input = step_9_idx)
        },
        error = function(e) {
          message(
            "Error in iteration ", step_9_iter_count, 
            " for index ", step_9_idx, ": ", e$message
          )
        }
      )
    }
    
    # Compute counts of each status
    step_9_fully_count     <- sum(global_master_dt$input_processing_status == "fully_processed")
    step_9_partial_count  <- sum(global_master_dt$input_processing_status == "partially_processed_and_moved_to_retry")
    step_9_total_count    <- sum(global_master_dt$input_processing_status == "total_error")
    step_9_progress_count <- sum(global_master_dt$input_processing_status == "in_progress")
    
    # Print status summary
    message(step_9_fully_count,     " entries fully processed")
    message(step_9_partial_count,   " entries had partial errors and were moved to retry")
    message(step_9_total_count,     " entries had total errors")
    message(step_9_progress_count,  " entries still being processed")
  }
  
  # Final summary when loop ends
  message("Master loop ends after ", step_9_iter_count, " iterations.")
  message(step_9_fully_count,    " entries fully processed")
  message(step_9_partial_count,  " entries had partial errors and were moved to retry")
  message(step_9_total_count,    " entries had total errors")
}


cat("Step 9 completed: Master loop defined. \n")

```

## Code Chunk 10: Preparing the Input, Initializing Progression Structures

### Summary:

This section initializes the core input data structures and applies pre-processing logic to clean and structure input URLs before the recursive scraping begins. It performs both string-based and date-based exclusions, logs all filtered-out URLs, and then sets up individual tracking tables and metadata for each valid sitemap. This ensures that all subsequent steps operate on curated input with corresponding data environments already initialized.

**Inputs:**  
- `step_2_input_dt`: a data table of cleaned sitemap URLs.  
- Global variables like `global_excluded_strings`, `global_date_start`, and `global_date_end`.

**Outputs:**  
- A cleaned input table (`step_10_clean_input_dt`) for sitemap processing.  
- New progression, output, and response log tables in the global environment per sitemap.  
- Updated entries in `global_master_dt`.  
- Logged exclusion metadata in `global_error_dt`.

### Functionality Details:

1. **String-based Exclusion:**  
   URLs matching any pattern in `global_excluded_strings` are filtered and logged with reason `"excluded_by_string"`.

2. **Date-based Exclusion:**  
   Remaining URLs are parsed using `step_5_2_date_check_link_func`, and any identified as `"out_of_range"` are logged as `"input_out_of_range"`.

3. **Logging of Exclusions:**  
   Both categories of excluded URLs are appended to `global_error_dt` with metadata including timestamps and exclusion reason.

4. **Progression Initialization:**  
   For each cleaned URL, empty `progression`, `output`, and `response_log` tables are created in `.GlobalEnv`. A root row is inserted into the progression table for each input.

5. **Master Table Entry:**  
   Each sitemap is added to `global_master_dt`, marking it as `"in_progress"` and initializing counters and status fields.

6. **Cleanup:**  
   All intermediate objects used during this step are explicitly removed from the environment to reduce clutter.

```{r Step 10: Preparing the Input, initializing progression structures}
# Step 10: Preparing the Input, initializing progression structures
step_10_input_dt <- step_2_input_dt  

# Exclude by string patterns
step_10_string_excluded_dt <- step_10_input_dt %>%
  filter(str_detect(layer_1_url, paste(global_excluded_strings, collapse = "|"))) %>%
  mutate(
    excluded_url_id = as.integer(layer_1_url_id),
    excluded_url    = layer_1_url,
    reason          = "excluded_by_string"
  )

# date-based filtering for remaining
step_10_remaining_dt <- step_10_input_dt %>%
  anti_join(step_10_string_excluded_dt, by = "layer_1_url_id") %>%
  rowwise() %>%
  mutate(
    date_res    = list(step_5_2_date_check_link_func(layer_1_url, global_date_start, global_date_end)),
    date_reason = date_res$reason
  ) %>%
  ungroup()

step_10_date_excluded_dt <- step_10_remaining_dt %>%
  filter(date_reason == "out_of_range") %>%
  mutate(
    excluded_url_id = as.integer(layer_1_url_id),
    excluded_url    = layer_1_url,
    reason          = "excluded_by_date"
  )

# log all exclusions into global_error_dt
global_error_dt <- rbind(
  global_error_dt,
  step_10_string_excluded_dt %>%
    transmute(
      domain_id       = domain_id,
      domain_url      = domain_url,
      layer_1_url_id  = layer_1_url_id,
      layer_1_url     = layer_1_url,
      error_url_id    = excluded_url_id,
      error_url       = excluded_url,
      parent_url_id   = 0L,
      root_tag        = "unknown",
      error_category  = "excluded_string",
      processed_flag  = TRUE,
      retry_flag      = FALSE,
      timestamp       = Sys.time(),
      source_function = "code_chunk_10",
      status_code     = NA_integer_
    ),
  step_10_date_excluded_dt %>%
    transmute(
      domain_id       = domain_id,
      domain_url      = domain_url,
      layer_1_url_id  = layer_1_url_id,
      layer_1_url     = layer_1_url,
      error_url_id    = excluded_url_id,
      error_url       = excluded_url,
      parent_url_id   = 0L,
      root_tag        = "unknown",
      error_category  = "input_out_of_range",
      processed_flag  = TRUE,
      retry_flag      = FALSE,
      timestamp       = Sys.time(),
      source_function = "code_chunk_10",
      status_code     = NA_integer_
    ),
  fill = TRUE
)

# prepare cleaned input table
step_10_clean_input_dt <- step_10_remaining_dt %>%
  filter(date_reason != "out_of_range") %>%
  select(domain_id, domain_url, layer_1_url_id, layer_1_url) %>%
  mutate(
    domain_id       = row_number(),
    layer_1_url_id  = row_number()
  )

# initialize individual progression / output / response tables and master entries
for (i in seq_len(nrow(step_10_clean_input_dt))) {
  did <- step_10_clean_input_dt$domain_id[i]
  dur <- step_10_clean_input_dt$domain_url[i]
  lid <- step_10_clean_input_dt$layer_1_url_id[i]
  url <- step_10_clean_input_dt$layer_1_url[i]

  prog_name <- paste0("sitemap_id_", lid, "_progression_dt")
  out_name  <- paste0("sitemap_id_", lid, "_output_dt")
  log_name  <- paste0("sitemap_id_", lid, "_response_log_dt")

  assign(prog_name, data.table(), envir = .GlobalEnv)
  assign(out_name,  data.table(), envir = .GlobalEnv)
  assign(log_name,  data.table(), envir = .GlobalEnv)

  root_entry <- data.table(
    domain_id                    = did,
    domain_url                   = dur,
    layer_1_url_id               = lid,
    layer_1_url                  = url,
    current_url_id               = 1L,
    current_url                  = url,
    parent_url_id                = 0L,
    processed                    = FALSE,
    processing_status            = "in_progress",
    sorted                       = "no",
    sort_place                   = NA_integer_,
    in_range                     = NA_character_,
    root_tag                     = "unknown",
    subsitemap_status            = NA_character_,
    sort_order                   = list(data.table()),
    subsitemap_progress          = NA_character_,
    pagination_group             = NA_character_,
    pagination_index             = NA_integer_,
    pagination_group_status      = NA_character_,
    timestamp                    = Sys.time()
  )
  assign(prog_name,
         rbind(get(prog_name, envir = .GlobalEnv), root_entry, fill = TRUE),
         envir = .GlobalEnv)

  global_master_dt <<- rbind(
    global_master_dt,
    data.table(
      domain_id               = did,
      domain_url              = dur,
      layer_1_url_id          = lid,
      layer_1_url             = url,
      input_processing_status = "in_progress",
      total_request_count     = 0L,
      total_urlsets_scraped   = 0L,
      last_checked            = Sys.time(),
      current_user_agent_id   = 0L,
      processing_flag         = "normal"
    ),
    fill = TRUE
  )
}
  
  # remove intermediate data tables
  rm(step_10_input_dt,
   step_10_string_excluded_dt,
   step_10_remaining_dt,
   step_10_date_excluded_dt,
   root_entry)


cat("Step 10 completed: individual progression, output and response tables initialized, master_dt updated.\n")

```

## Code Chunk 11: Calling the Master Loop

### Summary:

This final chunk executes the main control logic by invoking the master loop (`step_9_master_loop_func`) while redirecting all console output to a persistent log file. This allows for continuous monitoring of the scraping process, including iteration counts, processing status updates, and potential error messages. The loop processes all pending sitemaps until completion, based on progression status.

**Inputs:**  
- The previously initialized `global_master_dt` and associated environment-specific progression/output/log tables.  
- `step_1_logging_folder`: the directory for storing logs.

**Outputs:**  
- A text file `urlset_scraper_master_loop_log.txt` containing detailed logs of all iterations and statuses.  
- Updated progression and master tracking for all processed sitemaps.

### Functional Steps:

1. **Log File Preparation:**  
   Constructs a file path for a persistent log file within the logging directory.

2. **Console Redirection:**  
   Uses R's `sink()` function to redirect all subsequent output simultaneously to both the console and the log file for traceability.

3. **Execution of Master Loop:**  
   Calls the `step_9_master_loop_func()` which iteratively triggers the recursive sitemap processing for all valid entries.

4. **Cleanup:**  
   After loop execution, console redirection is terminated, and output behavior is reset to default.

```{r Step 11: Calling the Master Loop}
# Open a log file in the output folder and redirect console output to it
step_11_log_filepath <- file.path(step_1_logging_folder, "urlset_scraper_master_loop_log.txt")

# Start sinking both to file and console
sink(step_11_log_filepath, append = TRUE, split = TRUE)

# Invoke the master loop function
step_9_master_loop_func()

# Stop sinking and restore normal console output
sink()

```

## Step 12: Revalidating Index Sitemaps via Wayback CDX API

### Summary:
This code chunk integrates the Internet Archive’s CDX API to retrieve historical snapshots of each `<sitemapindex>` URL, re-extracts archived child links within a specified date window, and updates the internal progression and master tables accordingly. It operates on the global progression tables produced by previous steps and generates both a temporary Wayback progression table and a final overview table summarizing snapshot availability and new entries. The primary input is the set of progression data tables for each top-level sitemap, and the outputs include per-sitemap “wayback” progression tables (if snapshots are found) and an aggregated `step_12_overview_dt` data table. This process enhances coverage by back-filling any missed links from archived versions, ensuring a more complete corpus for sociotechnical analysis.

In this chunk, we first define a helper function to query the Wayback Machine CDX API for available snapshot timestamps of a given URL. We then assemble all `<sitemapindex>` entries from the global progression tables into a single data table. For each unique `layer_1_url_id`, we initialize an empty “wayback” progression table and iterate over each subsitemap URL, fetching snapshot timestamps and filtering them by the global date constraints. Valid snapshots are downloaded, parsed to extract `<loc>` elements, converted to new progression entries, and fed into the existing progression and master update functions. Finally, we compile a summary overview in `step_12_overview_dt` that records whether any snapshots were found and how many new entries were added.

#### Function: step_12_get_snapshots_func
The `step_12_get_snapshots_func` queries the CDX API endpoint for a JSON list of snapshot timestamps for a given URL, handling HTTP errors and rate limits explicitly. It performs an HTTP GET with query parameters for URL, output format, and requested fields, and checks for a 429 status to gracefully return an empty vector if rate-limited. Upon successful retrieval, it parses the JSON response, discards the header row, and returns a character vector of raw timestamp strings. This function encapsulates API interaction and enforces a simple contract: always return a vector (possibly empty) of timestamp identifiers for downstream processing.

```{r Step 12: Calling the wayback API and looking for snapshots of sitemaps}
# Define helper to fetch all snapshot timestamps from Wayback CDX API
step_12_get_snapshots_func <- function(url) {
  res <- httr::GET(
    "http://web.archive.org/cdx/search/cdx",
    query = list(url = url, output = "json", fl = "timestamp")
  )
  if (httr::status_code(res) == 429) {
    cat(sprintf("CDX API: 429 Rate Limit reached for URL: %s\n", url))
    return(character(0))
  }
  httr::stop_for_status(res)
  entries <- jsonlite::fromJSON(httr::content(res, as = "text", encoding = "UTF-8"))
  unlist(entries[-1])  # drop header row and return timestamps
}

# Collect all sitemapindex entries across progression tables
step_12_wayback_validation_dt <- data.table::rbindlist(
  lapply(
    ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_progression_dt$"),
    function(prog_name) {
      dt <- get(prog_name, envir = .GlobalEnv)
      data.table::copy(dt)[
        root_tag == "sitemapindex",
        .(domain_id, domain_url, layer_1_url_id, layer_1_url,
          current_url_id, current_url, parent_url_id, root_tag)
      ]
    }
  ),
  use.names = TRUE, fill = TRUE
)

# Initialize overview table for summary of Wayback integration
step_12_overview_dt <- data.table::data.table(
  layer_1_url_id = integer(),
  layer_1_url = character(),
  wayback_snapshot = logical(),
  added_wayback_entries = integer()
)

# Iterate by unique layer_1_url_id to process Wayback snapshots
for (lid in unique(step_12_wayback_validation_dt$layer_1_url_id)) {
  subset_dt <- step_12_wayback_validation_dt[layer_1_url_id == lid]
  snapshot_found <- FALSE
  total_new <- 0L

  prog_name <- paste0("sitemap_id_", lid, "_progression_dt")
  template_dt <- get(prog_name, envir = .GlobalEnv)[0]
  wayback_name <- paste0("sitemap_id_", lid, "_wayback_dt")
  assign(wayback_name, data.table::copy(template_dt), envir = .GlobalEnv)

  for (i in seq_len(nrow(subset_dt))) {
    row <- subset_dt[i]
    cat(sprintf("API Call: Requesting CDX snapshots for URL: %s\n", row$current_url))
    timestamps <- step_12_get_snapshots_func(row$current_url)
    Sys.sleep(4)  # pause required by CDX-API
    dates <- lubridate::ymd(substr(timestamps, 1, 8))
    sel_idx <- which(dates >= global_wayback_date_start & dates <= global_wayback_date_end)
    cat(sprintf("Snapshots in selected range: %d\n", length(sel_idx)))

    if (length(sel_idx) > 0L) {
      snapshot_found <- TRUE
      for (j in sel_idx) {
        ts <- timestamps[j]
        raw_url <- sprintf("http://web.archive.org/web/%sid_/%s", ts, row$current_url)
        resp <- try(httr::GET(raw_url, httr::timeout(30)), silent = TRUE)

        if (inherits(resp, "try-error") || httr::status_code(resp) >= 400) {
          cat(sprintf("Failed to load snapshot at: %s – skipping\n", raw_url))
          next
        }

        xml_text <- httr::content(resp, as = "text", encoding = "UTF-8")
        doc <- xml2::read_xml(xml_text)
        ns_map <- xml2::xml_ns_rename(xml2::xml_ns(doc), d1 = "ns")
        loc_nodes <- xml2::xml_find_all(doc, ".//ns:loc", ns = ns_map)
        links <- xml2::xml_text(loc_nodes)

        if (length(links) > 0L) {
          existing_dt <- get(prog_name, envir = .GlobalEnv)
          next_id <- max(existing_dt$current_url_id, na.rm = TRUE) + 1L
          new_rows <- lapply(seq_along(links), function(k) {
            data.table::data.table(
              domain_id = row$domain_id,
              domain_url = row$domain_url,
              layer_1_url_id = row$layer_1_url_id,
              layer_1_url = row$layer_1_url,
              current_url_id = next_id + k - 1L,
              current_url = links[k],
              parent_url_id = row$current_url_id,
              processed = FALSE,
              processing_status = "in_progress",
              sorted = "no",
              sort_place = NA_integer_,
              in_range = NA_character_,
              root_tag = "unknown",
              subsitemap_status = NA_character_,
              sort_order = list(data.table::data.table()),
              subsitemap_progress = NA_character_,
              pagination_group = NA_character_,
              pagination_index = NA_integer_,
              pagination_group_status = NA_character_,
              timestamp = Sys.time()
            )
          }) |> data.table::rbindlist()

          wayback_dt <- get(wayback_name, envir = .GlobalEnv)
          wayback_dt <- rbind(wayback_dt, new_rows, fill = TRUE)
          assign(wayback_name, wayback_dt, envir = .GlobalEnv)

          for (row_new in seq_len(nrow(new_rows))) {
            nr <- new_rows[row_new]
            step_7_1_progression_update(
              domain_id = nr$domain_id,
              domain_url = nr$domain_url,
              layer_1_url_id = nr$layer_1_url_id,
              layer_1_url = nr$layer_1_url,
              current_url = nr$current_url,
              parent_url_id = nr$parent_url_id,
              processed = nr$processed,
              processing_status = nr$processing_status,
              sorted = nr$sorted,
              sort_place = nr$sort_place,
              in_range = nr$in_range,
              root_tag = nr$root_tag,
              subsitemap_status = nr$subsitemap_status,
              subsitemap_progress = nr$subsitemap_progress,
              pagination_group = nr$pagination_group,
              pagination_index = nr$pagination_index,
              pagination_group_status = nr$pagination_group_status
            )
            total_new <- total_new + 1L
          }

          step_7_2_master_dt_update_func(
            domain_id = row$domain_id,
            domain_url = row$domain_url,
            l1_id = row$layer_1_url_id,
            layer_1_url = row$layer_1_url,
            request_increment = 0L,
            current_user_agent_id = NA_integer_
          )
        }
      }
    }
  }

  # Record summary info per layer_1_url_id
  step_12_overview_dt <- rbind(
    step_12_overview_dt,
    data.table::data.table(
      layer_1_url_id = lid,
      layer_1_url = subset_dt$layer_1_url[1],
      wayback_snapshot = snapshot_found,
      added_wayback_entries = total_new
    ),
    fill = TRUE
  )

  # Remove temp wayback dt if snapshot was found
  if (snapshot_found) rm(list = wayback_name, envir = .GlobalEnv)
}


cat("Step 12 completed: Indexsitemaps revalidated.\n")

```

## Step 13: Revalidating Out-of-Range URLSets via Wayback CDX API

This code chunk complements the previous Wayback integration by targeting all `<urlset>` entries that were excluded for being out of the defined date range. It retrieves archived versions of each out-of-range URLSET, parses any valid snapshots, and reinserts eligible links into the main output and progression tables. The primary input is the set of global progression tables filtered for `root_tag == "urlset" & in_range == "out_of_range"`, and the outputs include an updated `step_13_overview_dt` summary table and any newly scraped URLSET entries integrated via the existing scraper and master-update functions. This mechanism back-fills missing content from archival snapshots, ensuring a more temporally complete corpus for downstream sociotechnical analysis.

### Summary:
This chunk first enumerates all progression tables in the global environment and filters them for `<urlset>` entries that were marked “out_of_range.” It then iterates per unique `layer_1_url_id`, invoking the previously defined `step_12_get_snapshots_func` to obtain CDX snapshot timestamps and selecting those within the `global_wayback_date_start` and `global_wayback_date_end` window. For each valid snapshot, it constructs the Wayback Machine URL, retrieves and parses the XML, and—if not already present—processes it through `step_7_4_urlset_scraper_func` to extract `<loc>` links. Finally, it updates the global master table via `step_7_2_master_dt_update_func` and records per-sitemap summary metrics in `step_13_overview_dt`.

#### Inputs:
- Global progression tables named `sitemap_id_<n>_progression_dt`, filtered for `root_tag == "urlset" & in_range == "out_of_range"`.
- Date boundaries `global_wayback_date_start` and `global_wayback_date_end`.
- Helper functions: `step_12_get_snapshots_func`, `step_7_4_urlset_scraper_func`, and `step_7_2_master_dt_update_func`.

#### Outputs:
- An aggregated data table `step_13_wayback_validation_urlset_dt` listing all out-of-range URLSET entries.
- A summary overview `step_13_overview_dt` containing `layer_1_url_id`, `layer_1_url`, a boolean `wayback_snapshot`, and the count `added_wayback_entries`.
- Updated output tables `sitemap_id_<n>_output_dt` enriched with any newly scraped URLSET content.
- Corresponding updates to the global master and progression tables for each successfully retrieved snapshot.

```{r step 13: Calling the wayback API and looking for snapshots of urlsets }
# Load all progression tables and extract URLSET entries that were out-of-range
prog_names <- ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_progression_dt$")
list_urlset_dt <- lapply(prog_names, function(prog_nm) {
  prog_dt <- get(prog_nm, envir = .GlobalEnv)
  # Filter for urlset root tags with out-of-range dates
  prog_dt[root_tag == "urlset" & in_range == "out_of_range",
          .(domain_id,
            domain_url,
            layer_1_url_id,
            layer_1_url,
            current_url_id,
            current_url,
            parent_url_id,
            root_tag)]
})
# Combine into a single data.table
step_13_wayback_validation_urlset_dt <- data.table::rbindlist(
  list_urlset_dt, use.names = TRUE, fill = TRUE
)

# Initialize overview table
step_13_overview_dt <- data.table::data.table(
  layer_1_url_id = integer(),
  layer_1_url = character(),
  wayback_snapshot = logical(),
  added_wayback_entries = integer()
)

# Iterate over each unique layer_1_url_id
for (lid in unique(step_13_wayback_validation_urlset_dt$layer_1_url_id)) {
  subset_dt <- step_13_wayback_validation_urlset_dt[layer_1_url_id == lid]
  snapshot_found <- FALSE
  total_new <- 0L

  for (i in seq_len(nrow(subset_dt))) {
    row <- subset_dt[i]

    cat(sprintf("API Call: Requesting CDX snapshots for URL: %s\n", row$current_url))
    timestamps <- step_12_get_snapshots_func(row$current_url)
    dates <- lubridate::ymd(substr(timestamps, 1, 8))
    sel_idx <- which(dates >= global_wayback_date_start &
                     dates <= global_wayback_date_end)
    cat(sprintf("Snapshots in selected range: %d\n", length(sel_idx)))

    if (length(sel_idx) > 0L) {
      snapshot_found <- TRUE

      for (j in sel_idx) {
        ts <- timestamps[j]
        wayback_url <- sprintf("http://web.archive.org/web/%sid_/%s", ts, row$current_url)
        resp <- try(httr::GET(wayback_url, httr::timeout(30)), silent = TRUE)

        if (inherits(resp, "try-error") || httr::status_code(resp) >= 400L) {
          cat(sprintf("Failed to load snapshot at: %s – skipping\n", wayback_url))
          next
        }

        out_nm <- paste0("sitemap_id_", lid, "_output_dt")
        out_dt <- get(out_nm, envir = .GlobalEnv)

        if (!wayback_url %in% out_dt$urlset_url) {
          # Report valid snapshot URL
          cat(sprintf("Valid snapshot found in range: %s\n", wayback_url))

          # Process with step_7_4 function
          res <- step_7_4_urlset_scraper_func(
            url               = wayback_url,
            http_response     = resp,
            xml_doc           = NULL,
            global_date_start = global_date_start,
            global_date_end   = global_date_end,
            domain_id         = row$domain_id,
            domain_url        = row$domain_url,
            layer_1_url_id    = lid,
            layer_1_url       = row$layer_1_url,
            current_url_id    = row$current_url_id,
            parent_url_id     = row$parent_url_id
          )

          if (!is.null(res) && isTRUE(res$in_range)) {
            total_new <- total_new + 1L
          }
        }

        step_7_2_master_dt_update_func(
          domain_id             = row$domain_id,
          domain_url            = row$domain_url,
          l1_id                 = lid,
          layer_1_url           = row$layer_1_url,
          request_increment     = 0L,
          current_user_agent_id = NA_integer_
        )
      }
    }
  }

  step_13_overview_dt <- rbind(
    step_13_overview_dt,
    data.table::data.table(
      layer_1_url_id        = lid,
      layer_1_url           = subset_dt$layer_1_url[1],
      wayback_snapshot      = snapshot_found,
      added_wayback_entries = total_new
    ),
    fill = TRUE
  )
}


cat("Step 13 completed: Urlsets out of range revalidated.\n")

```

## Code Chunk 14: Calling the Master Loop for Wayback Links

### Summary:
This chunk re-invokes the master processing loop to handle any new sitemap or URLSET entries added from the Wayback snapshots. It redirects output to a dedicated log file (`urlset_scraper_master_loop_log__wayback.txt`) while still printing to the console, ensuring traceable execution.

#### Inputs:
- Updated global progression and output tables containing Wayback‐derived entries.
- The `step_9_master_loop_func` itself, which orchestrates recursive sitemap processing.

#### Outputs:
- Continued updates to `global_master_dt`, progression tables, and output tables as new links are processed.
- Detailed logs in the specified Wayback‐focused log file.

```{r: Step 14: Calling the master loop again to process the new wayback links}

# Define the log file path for step 14
step_14_log_filepath <- file.path(step_1_logging_folder, "urlset_scraper_master_loop_log__wayback.txt")

# Redirect all console output to the log file and the console
sink(step_14_log_filepath, append = TRUE, split = TRUE)

# Invoke the master loop function to process any remaining sitemap entries
step_9_master_loop_func()

# Stop redirecting and restore normal console output
sink()

```

## Code Chunk 15: Wrangling and Saving Outputs, Generating Retry Progression Tables

### Summary:

This final processing step performs post-scraping wrangling and persistence operations. It systematically cleans and consolidates data, prepares structures for retry operations, and saves all relevant objects in `.rds` format. This ensures that failed or incomplete operations can be retried and that all progression information is archived for transparency and reproducibility.

**Inputs:**  
- All `*_progression_dt`, `*_response_log_dt`, and `*_output_dt` objects in the global environment.  
- Global tracking objects: `global_master_dt`, `global_error_dt`.

**Outputs:**  
- Updated global error log (`global_error_dt`) including string-based exclusions.  
- Retry structures: `global_retry_master_dt`, individual `*_retry_progression_dt` tables.  
- `.rds` files for all major progression, output, and log tables saved in `step_1_output_folder`.

### function: step_15_wrangle_and_save_func

This function executes the complete post-processing logic in six stages:

1. **Remove Sort Order:**  
   All `sort_order` columns are removed from `*_progression_dt` tables to reduce object size before serialization.

2. **Log String Exclusions:**  
   Entries with `processing_status == "excluded_by_string"` are appended to `global_error_dt` as finalized errors.

3. **Clean Empty Response Logs:**  
   Response log tables without any entries are deleted to reduce redundancy.

4. **Generate Retry Master Table:**  
   A filtered copy of `global_master_dt` is created containing only partially processed sitemaps. Status flags and counters are reset to enable retry.

5. **Construct Retry Progression Tables:**  
   For each sitemap eligible for retry, a new progression table is assembled from logged error responses (`retry_flag == TRUE`), including metadata such as status codes and response body snippets.

6. **Serialize All Objects:**  
   All relevant objects—including progression, output, response, and retry tables—are saved as `.rds` files within the specified output directory for later reuse.


```{r Step 15: Wrangling and saving outputs, generating retry_progression_dts}
# Step 15: Wrangle Outputs and Save
# This chunk removes the "sort_order" column, collects excluded-by-string errors,
# cleans empty logs, builds retry tables, and saves all relevant objects.
step_15_wrangle_and_save_func <- function() {
  # 1. Remove "sort_order" from all progression tables
  prog_names <- ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_progression_dt$")
  for (nm in prog_names) {
    dt <- get(nm, envir = .GlobalEnv)
    if ("sort_order" %in% names(dt)) {
      dt[, sort_order := NULL]
    }
    assign(nm, dt, envir = .GlobalEnv)
  }

  # 2. Collect "excluded_by_string" entries into global_error_dt
  for (nm in prog_names) {
    dt   <- get(nm, envir = .GlobalEnv)
    excl <- dt[processing_status == "excluded_by_string", ]
    if (nrow(excl) > 0L) {
      start_id <- nrow(global_error_dt) + 1L
      new_ids  <- seq(start_id, length.out = nrow(excl))
      err_dt <- data.table(
        domain_id       = excl$domain_id,
        domain_url      = excl$domain_url,
        layer_1_url_id  = excl$layer_1_url_id,
        layer_1_url     = excl$layer_1_url,
        error_url_id    = new_ids,
        error_url       = excl$current_url,
        parent_url_id   = excl$parent_url_id,
        root_tag        = excl$root_tag,
        error_category  = "excluded_string",
        processed_flag  = TRUE,
        retry_flag      = FALSE,
        timestamp       = excl$timestamp,
        status_code     = excl$status_code,
        source_function = "step_8"
      )
      global_error_dt <<- unique(rbind(global_error_dt, err_dt, fill = TRUE))
    }
  }

  # 3. Remove empty response-log tables
  resp_names <- ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_response_log_dt$")
  for (nm in resp_names) {
    dt <- get(nm, envir = .GlobalEnv)
    if (nrow(dt) == 0L) {
      rm(list = nm, envir = .GlobalEnv)
    }
  }

  # 4. Build global_retry_master_dt
  global_retry_master_dt <<- copy(global_master_dt[input_processing_status == "partially_processed_and_moved_to_retry"])
  if (nrow(global_retry_master_dt) > 0L) {
    global_retry_master_dt[, `:=`(
      input_processing_status = "in_progress",
      total_request_count     = 0L,
      total_urlsets_scraped   = 0L,
      current_user_agent_id   = 0L,
      last_checked            = as.POSIXct(NA),
      processing_flag         = "normal"
    )]
  }

  # 5. Create retry progression tables
  for (i in seq_len(nrow(global_retry_master_dt))) {
    lid    <- global_retry_master_dt$layer_1_url_id[i]
    resp_nm <- paste0("sitemap_id_", lid, "_response_log_dt")
    if (!exists(resp_nm, envir = .GlobalEnv)) next
    resp_dt <- get(resp_nm, envir = .GlobalEnv)[retry_flag == TRUE]
    if (nrow(resp_dt) == 0L) next

    retry_prog_nm <- paste0("sitemap_id_", lid, "_retry_progression_dt")
    cols <- c(
      "domain_id","domain_url","layer_1_url_id","layer_1_url",
      "current_url_id","current_url","parent_url_id","processed",
      "processing_status","sorted","sort_place","in_range",
      "root_tag","subsitemap_status","subsitemap_progress",
      "pagination_group","pagination_index","pagination_group_status",
      "timestamp",
      "http_status_code","http_status_message",
      "response_header_snippet","response_body_snippet",
      "response_category","action_taken"
    )
    
    out_dt <- data.table(
      domain_id = integer(),
      domain_url = character(),
      layer_1_url_id = integer(),
      layer_1_url = character(),
      current_url_id = integer(),
      current_url = character(),
      parent_url_id = integer(),
      processed = logical(),
      processing_status = character(),
      sorted = character(),
      sort_place = integer(),
      in_range = character(),
      root_tag = character(),
      subsitemap_status = character(),
      subsitemap_progress = character(),
      pagination_group = character(),
      pagination_index = integer(),
      pagination_group_status = character(),
      timestamp = as.POSIXct(character()),
      http_status_code = integer(),
      http_status_message = character(),
      response_header_snippet = character(),
      response_body_snippet = character(),
      response_category = character(),
      action_taken = character()
    )
    
    for (j in seq_len(nrow(resp_dt))) {
      r <- resp_dt[j]
      row <- data.table(
        domain_id               = r$Domain_id,
        domain_url              = r$Domain_url,
        layer_1_url_id          = r$Layer_1_url_id,
        layer_1_url             = r$Layer_1_url,
        current_url_id          = r$requested_url_id,
        current_url             = r$requested_url,
        parent_url_id           = NA_integer_,
        processed               = FALSE,
        processing_status       = "in_progress",
        sorted                  = "no",
        sort_place              = NA_integer_,
        in_range                = NA_character_,
        root_tag                = "unknown",
        subsitemap_status       = NA_character_,
        subsitemap_progress     = NA_character_,
        pagination_group        = NA_character_,
        pagination_index        = NA_integer_,
        pagination_group_status = NA_character_,
        timestamp               = r$timestamp,
        http_status_code        = r$http_status_code,
        http_status_message     = r$http_status_message,
        response_header_snippet = r$response_header_snippet,
        response_body_snippet   = r$response_body_snippet,
        response_category       = r$response_category,
        action_taken            = r$action_taken
      )
      out_dt <- rbind(out_dt, row, fill = TRUE)
    }
    assign(retry_prog_nm, out_dt, envir = .GlobalEnv)
  }

  # 6. Save all objects as .rds
  save_list <- c(
    ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_progression_dt$"),
    ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_output_dt$"),
    ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_response_log_dt$"),
    ls(envir = .GlobalEnv, pattern = "^sitemap_id_[0-9]+_retry_progression_dt$"),
    "global_master_dt","global_error_dt", "global_retry_master_dt"
  )
  for (nm in save_list) {
    obj <- get(nm, envir = .GlobalEnv)
    saveRDS(obj, file = file.path(step_1_output_folder, paste0(nm, ".rds")))
  }
}

step_15_wrangle_and_save_func()


cat("Step 15 completed: All date cleaned and saved.\n")

```


